---
title: "MU_final"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Packages + Read in Data

```{r, include = TRUE}
library(tidyverse)
library(magrittr)
library(here)
library(data.table)
library(MASS)
library(knitr)
library(finalfit)
library(stargazer)
library(lubridate)
library(mapview)
library(sf)
library(caret)
# read in csv
thesis_data <- read_csv(here::here("DATA","thesis-data.csv"))
```

# Wrangling

```{r, echo = TRUE}
# Split Data
MU <- thesis_data %>%
  filter(prop_type == "Mixed Use")

#-------------------------------------------------------------------------

# Make a string of constraints and percent canopy names called "con_names"
clean <- SFR %>%
  dplyr::select(conECSI, conLUST, 
                conHist, conHistLdm, conNatAm,
                conCovrly, conPovrly,
                conAirHgt, conHeliprt, conNoise,
                conGW,
                conLSHA, conSLIDO, conFld100, conSlp25, 
                conSewer, conStorm, conWater,
                conWetland,
                conInstit, conPrvCom, conPubOwn,
                conView,
                conTranCap, conTranInt, conTranSub)
clean_names <- names(clean)
con_names <- paste(clean_names, collapse = " + ")

# switch the NAs in the constraints to 0s
to0 <- function(x){ifelse(is.na(x), 0, x)}

#-------------------------------------------------------------------------

# Format SFR Dataframe: 
# Select variables, mutate filtering parameters. No actual filtering done at this point, all SFR vars kept. 
MUtest1 <- MU %>%
  dplyr::select(-c(OWNER2, OWNER3, OWNERZIP, 
            MKTVALYR1, MKTVALYR2,
            BLDGVAL1, BLDGVAL2,
            LANDVAL1, LANDVAL2,  
            TOTALVAL1, TOTALVAL2,
            MS_GRADE, ES_GRADE,
            LEGAL_DESC, 
            LANDUSE, 
            BEDROOMS, ACC_STATUS, 
            NAME, COMMPLAN, SHARED, 
            COALIT, HORZ_VERT, AUDIT_NBRH, 
            MIDDLE_SCH,  Category, SOURCE, 
            FRONTAGE, COUNTY, YEARBUILT, bldgtype)) %>%
  mutate(top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
         MKTVALYR3 = case_when(MKTVALYR3 != 2018 ~ 2017, 
                                         TRUE ~ 2018),
         price_diff = SALEPRICE - LANDVAL3, 
         price_ratio = SALEPRICE/LANDVAL3 * 100,
         vacant_dummy = as.numeric(PRPCD_DESC == "VACANT LAND"),
         sale_z_old = case_when(sale_zone == "EX" ~ "Central Employment",
                                   sale_zone == "CS" ~ "Storefront Commercial",
                                   sale_zone == "CM" ~ "Mixed Commercial/Residential",
                                   sale_zone == "CG" ~ "General Commercial",
                                   sale_zone == "CO1" | sale_zone == "CO2" ~ "Office Commercial",
                                   sale_zone == "CN1" | sale_zone == "CN2" ~ "Neighborhood Commercial",                                 
                                   sale_zone == "CM1" ~ "Mixed Use 1",
                                   sale_zone == "CM2" ~ "Mixed Use 2",
                                   sale_zone == "CM3" ~ "Mixed Use 3",
                                   sale_zone == "CX" ~ "Central Commercial",
                                   TRUE ~ "Mixed Use"),
         sale_z_new = case_when(sale_zone == "EX" ~ "Mixed Use 3", #unclear, depends on location
                                   sale_zone == "CS" ~ "Mixed Use 2",
                                   sale_zone == "CM" ~ "Mixed Use 2", 
                                   sale_zone == "CG" ~ "Commercial Employment", #corridor vs center CM2 vs CE
                                   sale_zone == "CO1" ~ "Mixed Use 1",
                                sale_zone == "CO2" ~ "Mixed Use 2",
                                   sale_zone == "CN1" | sale_zone == "CN2" ~ "Mixed Use 1",                                 
                                   sale_zone == "CM1" ~ "Mixed Use 1",
                                   sale_zone == "CM2" ~ "Mixed Use 2",
                                   sale_zone == "CM3" ~ "Mixed Use 3",
                                   sale_zone == "CX" ~ "Mixed Use 3",
                                   TRUE ~ "Mixed Use 2"),
         owner_state_dummy = case_when(OWNERSTATE == "OR" ~ "1",
                                    TRUE ~ "0"),
         totalsqft_sqd = totalsqft*totalsqft,
         taxlot_area_sqd = taxlot_area*taxlot_area,
         n_fireplaces = replace_na(n_fireplaces, 0),
         fireplace_dum = as.numeric(n_fireplaces > 0),
         ADUdummy = as.numeric(ADUdummy > 0),
         total_canopy_cov = replace_na(total_canopy_cov, 0),
         canopy_dum = as.numeric(total_canopy_cov > 0))

#-------------------------------------------------------------------------

#garage sqft
MUgar_sqft_sum <- MUtest1 %>%
  dplyr::select(matches("gar"), matches("car")) %>%
  rowSums()

# basement sqft
MUbsmt_sqft_sum <- MUtest1 %>%
  dplyr::select(matches("bsmt")) %>%
  dplyr::select(-c("BSMT PARKING","BSMT GAR")) %>%
  rowSums()

# creating zone change dummy
MUzone_test <- MUtest1 %>%
  dplyr::select(matches("zone"), -c(ZONE_DESC_aug2016, ZONE_DESC_aug2018, ZONE_DESC_feb2018, `Zone Description`, sale_zone)) %>%
  mutate_all(str_replace, pattern = "R", replacement = "") %>%
  mutate_all(funs(as.numeric)) %>%
  rowSums()

# adding new vars to MUtest1
MUtest1 %<>%
  mutate(garage_sqft = MUgar_sqft_sum,
         garage_dum = as.numeric(garage_sqft > 0),
         bsmt_sqft = MUbsmt_sqft_sum,
         bsmt_dum = as.numeric(bsmt_sqft > 0),
         sum_z = MUzone_test,
         avg_z = sum_z/9,
         z_change = case_when(avg_z == 5 ~ 0,
                                      TRUE ~ 1))

#-------------------------------------------------------------------------

# Clean SFR dataframe: 
# remove based on filtering parameters, set NAs as zero, add in improvements
MUtest2 <- MUtest1 %>%
  dplyr::select(-c(matches("zone"))) %>%
  mutate_at(vars(clean_names), to0) %>%
  mutate(arms_length100 = case_when(price_ratio > 100 ~ TRUE,
                                 TRUE ~ FALSE),
         arms_length20 = case_when(price_ratio > 20 ~ TRUE,
                                 TRUE ~ FALSE),
         yearbuilt = na_if(yearbuilt, 0),
         saleprice_zero = case_when(SALEPRICE == 0 ~ TRUE,
                                 TRUE ~ FALSE),
         saledate = mdy(saledate), 
         year_sold = year(saledate),
         age_sold = year_sold - yearbuilt,
         percent_vacant = percent_vacant*100,
         SALEPRICElog = log(SALEPRICE),
         FLOORS = replace_na(FLOORS, 1),
         FLOORS = case_when(FLOORS == 0 ~ 1,
                            TRUE ~ FLOORS),
         totalsqft_imp = case_when(is.na(totalsqft) ~ BLDGSQFT,
                                   TRUE ~ totalsqft),
         totalsqft_sqd_imp = totalsqft_imp*totalsqft_imp,
         totalsqft_na = case_when(is.na(totalsqft) ~ FALSE,
                                   TRUE ~ TRUE),
         age_sold_na = is.na(age_sold),
         maxheight = na_if(maxheight, 0),
         volume = na_if(volume, 0),
         bldguse = na_if(bldguse, 0)) %>%
  filter(totalsqft != 0, # 30 obs
         age_sold >= 0, # 20 obs but most negative were -1 to -3 so not that bad. could recode but this likely means that its vacant land right now....
         vacant_dummy == FALSE, # too much of a fucking hassle, much too different from improved lots. would likely skew results in favor of taxlot area (but is that a problem? coud be a way of checking for future expectations, especially since zoning is out of the question)
         SALEPRICE > 30000, # sale price == 0 has to be a recording error somewhere down the line. most of the sale price less than 30,000 are not arms length transactions 
         yearbuilt > 1500,
         arms_length20 == TRUE,
         BLDGVAL3 > 50000, #no vacant land
         f_baths > 0 | h_baths > 0,
         totalsqft > 600)

#==============================================
# things to worry about:

# DONE
#   + drop small total sqft --- look in maps NOPE all good
# drop totalsqft == 0 after looking at maps,  note they dont actually ahave a building area of zero, just reported wrong for some reason
#   + top 1 --- not doing
#   + vacant dummy --- doing
#   + owner state dummy --- not doing
#   + remove sale price of zero
#   + remove sale price of zero or less than 30,000 --- doing zero, check less in maps
#   + drop floors keep existing floors, recode floors == 0 to be NA
#   + dont use UNITS in regressions -- very messed up and only occassionally reports correct units (this is based on pop cd desc of multifamily props)
# then add in everything else --NO WAY IN HELL KEEPING IMPROVEMENTS IN MODEL but dont drop na observations

# TO DO 
# fixed effects for propcd desc vs new zoning vs old zoning
#==============================================

# FOR DATA EQUALS ZERO!!!!!!!!!!

        # dataset1 : floors == zero dropped, NA floors automatically dropped
        # dataset2: floors == zero recoded to one, NA floors automatically dropped, check whether any building value == zero
        
        # units == zero: a total mess
#==============================================
### Looking at NA's systematically 

mary <- MUtest1 %>% 
  filter(vacant_dummy == TRUE)
brady <- 2008 - nrow(mary)
brady
brady/2008

#-------------------------------------------------------------------------

# Select final relevant variables
MUdat1 <- MUtest2 %>%
  dplyr::select(
    STATE_ID, RNO, PROPERTYID, TLID, 
    OWNER1, owner_state_dummy, 
    SITEADDR, SITEZIP, TAXCODE, PRPCD_DESC, 
    MKTVALYR3, LANDVAL3, BLDGVAL3, TOTALVAL3, 
    arms_length100, arms_length20, 
    saledate, SALEPRICE, SALEPRICElog, saleprice_zero,
    age_sold, age_sold_na,
    totalsqft, totalsqft_sqd, totalsqft_imp, totalsqft_sqd_imp, totalsqft_na,
    taxlot_area, taxlot_area_sqd, 
    FLOORS,  
    UNITS, volume,
    maxheight, bldguse, 
    f_baths, h_baths,
    n_fireplaces, fireplace_dum, ADUdummy, 
    garage_sqft, garage_dum, bsmt_sqft, bsmt_dum, 
    percent_vacant, vacant_dummy,
    pct_canopy_cov, total_canopy_cov, canopy_dum, 
    zone_change = z_change, sale_z_old, sale_z_new, 
    CN_score, Neighborhood = MapLabel, HIGH_SCH, ELEM_SCH, dist_cityhall, dist_ugb,
    contains("con"), contains("pct")) %>%
  dplyr::select(-c("CONCRETE", "FIN SECOND", "PAVING/CONCRETE ONLY", "UNF SECOND", "conFldway", "pct_conFldway")) 



```

# Exploration

```{r}

# A Look at the Dataset

salma <- summary(MUdat1) # notes in thesis notebook

# Correlation -- Scatterplots

controls <- MUtest2 %>%
  dplyr::select(price_diff, pct_canopy_cov, taxlot_area, yearbuilt, totalsqft, dist_ugb, dist_cityhall, percent_vacant, CN_score, 
         SALEPRICE)
nm <- names(controls)

correlation <- cor(controls, use = "pairwise.complete.obs")
#takes only obs for which both vars are not NA


for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(y = nm[length(nm)], x = nm[i])) + 
    geom_point(alpha = 0.1) +
    geom_smooth())
}


ggplot(MUtest2, aes(y = SALEPRICE, x = TOTALVAL3)) + 
    geom_point()

ggplot(MUtest2, aes(y = log(SALEPRICE), x = taxlot_area)) + 
    geom_point()

# Outliers -- Box Plots

# best for discrete x

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(y = nm[length(nm)], x = nm[i])) + 
    geom_boxplot(alpha = 0.1))
}

# Distribution of Constraints -- Density Plots

# Now to check the linearity of the variables it is a good practice to plot distribution graph and look for skewness of features. Kernel density estimate (kde) is a quite useful tool for plotting the shape of a distribution.

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(x = nm[i])) + 
    geom_histogram(bins = 50))
}


```


```{r}
MUtest2 %>%
  filter(SALEPRICE > 100000000)


taxlots_pruned %>%
  filter(SALEPRICE > 50000000) %>%
  mapview(zcol = c("SALEPRICE"), 
        layer.name = c("Natheli"))

```


# Summary Statistics

```{r, echo = TRUE}

MUsumdat_controls <- MUdat1 %>%
    # Select and rename
    dplyr::select(
        `Assessed Land Value (2017)` = LANDVAL3,
        `Assessed Building Value (2017)` = BLDGVAL3,
        `Total Assessed Value (2017)` = TOTALVAL3,
        
        `Sale Price` = SALEPRICE,
        `Log Sale Price` = SALEPRICElog,
        `Age When Sold` = age_sold,
        `Building Footprint (sqft)` = totalsqft,
        `Building Footprint Squared (sqft)` = totalsqft_sqd,
        `Taxlot Area (sqft)` = taxlot_area,
        `Taxlot Area Squared (sqft)` = taxlot_area_sqd,
        `Building Volume` = volume,
        `Number of Floors` = FLOORS,
        `Maximum Building Height (ft)` = maxheight,
        
        `Full Baths` = f_baths,
        `Half Baths` = h_baths,
        
        `Vacant Properties in 200ft Radius (%)` = percent_vacant,
        `Vacant Dummy` = vacant_dummy,
        `Canopy Cover (% of lot)` = pct_canopy_cov,
        `Canopy Cover Dummy` = canopy_dum,
        `Complete Neighborhoods Score (0-100)` = CN_score,
        `Distance to Central Business District (ft)` = dist_cityhall,
        `Distance to Urban Growth Boundary (ft)` = dist_ugb)


MUsumdat_constraints <- MUdat1 %>%
    # Select and rename
    dplyr::select(
        `DEQ Environmental Cleanup Sites (ECSI)` = conECSI,
        `DEQ Leaking Underground Storage Tank Cleanup Sites (LUST)` = conLUST,
        
        `Historic and Conservation Districts` = conHist,
        `Historic and Conservation Landmarks` = conHistLdm,
        `Areas Requiring Archeological Scan or Consultation with Tribes` = conNatAm,
        
        `Percent of Preservation Zones` = pct_conPovrly,
        `Percent of Conservation Zones` = pct_conCovrly,
        
        `Approach and Departure Cones` = conAirHgt,
        `Helipad Landing` = conHeliprt,
        `Airport Noise` = conNoise,
        
        `Greenway` = conGW,
        
        `DOGAMI Landslide Hazard Area` = conLSHA,
        `DOGAMI Digital Landslide Database (SLIDO)` = conSLIDO,
        `FEMA 100-Year Floodplain Map` = conFld100,
        `Slopes Over 25% Incline` = conSlp25,
        
        `Sewer System` = conSewer,
        `Stormwater System` = conStorm,
        `Water System` = conWater,
        
        `Wetlands` = conWetland,
        
        `Institutional Campuses` = conInstit,
        `Private/Common Open Space` = conPrvCom,
        `Publicly Owned Lots` = conPubOwn,

        `Scenic Views` = conView,
        
        `Traffic Volume Exceeds Capacity` = conTranCap,
        `ODOT Highway Interchanges` = conTranInt,
        `Substandard and Unimproved Streets` = conTranSub
        )

MUdat1 %>%
  filter(BLDGVAL3 < 100000) %>%
ggplot(aes(x = BLDGVAL3)) + 
  geom_histogram(bins = 50)


stargazer(
  as.data.frame(MUsumdat_controls),
  summary = TRUE,
  summary.stat = c("mean", "sd", "min", "max"),
  summary.logical = TRUE,
  digits = 2,
  type = "html",
  style = "io",
  title = "Mixed-use Residential Summary Statistics: Controls",
  out = "sumstats_controls_mu.htm")

stargazer(
  as.data.frame(MUsumdat_constraints),
  summary = TRUE,
  summary.stat = c("mean", "sd", "min", "max"),
  summary.logical = TRUE,
  digits = 2,
  type = "html",
  style = "io",
  title = "Mixed-use Summary Statistics: Development Constraints",
  out = "sumstats_constraints_mu.htm")

```

# Regression 2: Arms Length Variation

```{r}

MUbase_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy +  
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUbase_log.mod <- lm(MUbase_log, MUdat1)
summary(MUbase_log.mod)


# ALL OBSERVATIONS, NAs IN, ZEROs IN -----------------------------

MUsz_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUsz_log.mod <- lm(MUsz_log, MUdat1)
summary(MUsz_log.mod)

# remove ecsi, coverly, poverly, noise, gw, slido, JUST FOR VIF TEST
clean_vif <- MU %>%
  dplyr::select(conLUST, 
                conHist, conHistLdm,
                conAirHgt,
                conLSHA, conFld100, conSlp25, 
                conStorm, conWater,
                conTranSub)
clean_vif_names <- names(clean_vif)
con_names_vif <- paste(clean_vif_names, collapse = " + ")

# took out canopy cover and vacancy dummy
MUbase_log_vif = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + 
                         taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names_vif))

MUbase_log_vif.mod <- lm(MUbase_log_vif, MUdat1)
summary(MUbase_log_vif.mod)
alias(MUbase_log_vif.mod)
car::vif(MUbase_log_vif.mod, singular.ok = TRUE)


# 20% CUT -----------------------------
MUdat20 <- MUdat1 %>% # only removed 3 obs lmao
  filter(arms_length20 == TRUE)
MUbase20_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + 
                         f_baths + h_baths + 
                         vacant_dummy + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUbase20_log.mod <- lm(MUbase20_log, MUdat1)
summary(MUbase20_log.mod)


# 100% CUT -----------------------------
MUdat100 <- MUdat1 %>% # removed 78 obs
  filter(arms_length100 == TRUE)
MUbase100_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUbase100_log.mod <- lm(MUbase100_log, MUdat100)
summary(MUbase100_log.mod)

# add in volume -----------------------------

MUvol_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + volume + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUvol_log.mod <- lm(MUvol_log, MUdat100)
summary(MUvol_log.mod)


# Regression 4: LLCs
stargazer(
  MUbase_log.mod, MUbase20_log.mod, MUbase100_log.mod, MUsz_log.mod,
  title = "Regression 2: Arms Length",
  keep.stat = c("rsq", "adj.rsq"),
  notes.align = "l",
  type="html", 
  out="MUmods_base.htm")
```

# Regression 3: Age and Sale Price
```{r}

# REMOVE SALE PRICE = 0  -----------------------------

# REMOVE AGE_SOLD = NA -----------------------------

# REMOVE TOTALSQFT = NA -----------------------------

# IMPUTE TOTALSQFT -----------------------------

MUsfimp_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd_imp + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUsfimp_log.mod <- lm(MUsfimp_log, MUdat1)
summary(MUsfimp_log.mod)

```


# Regression 4: Floors

```{r}

# FLOORSone - all nas and zeros recoded to one -----------------------------

MUfloorsone_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORSone + UNITS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUfloorsone_log.mod <- lm(MUfloorsone_log, MUdat1)
summary(MUfloorsone_log.mod)


# FLOORSzero dont include floors  -----------------------------


MUfzero_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         UNITS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         vacant_dummy + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUfzero_log.mod <- lm(MUfzero_log, MUdat1)
summary(MUfzero_log.mod)


# Regression 4: LLCs
stargazer(
  MUbase_log.mod, MUfloors_log.mod, MUfloorsone_log.mod, MUfloorsna_log.mod, MUfzero_log.mod,
  title = "Regression 2: Arms Length",
  column.labels = c("base", "floors", "floorsone", "floorsna", "floorszero"),
  keep.stat = c("rsq", "adj.rsq"),
  notes.align = "l",
  type="html", 
  out="MUmods_floors.htm")

```


# Regression 5: Improvements

```{r}
# MAXHEIGHT = NA and BLDGUSE = NA -----------------------------



# F_BATHS AND H_BATHS = NA -----------------------------


# NO UNITS -----------------------------

# Regression 1: Pre-analysis Regression

```{r}
# LOG REGRESSION KITCHEN SINK-----------------------------------------

MUpreanalysis_log = formula(paste0("SALEPRICElog ~ 
                          owner_state_dummy + SITEZIP + TAXCODE + PRPCD_DESC + age_sold + 
                         totalsqft + totalsqft_sqd + taxlot_area + taxlot_area_sqd + 
                         volume + FLOORS + UNITS + maxheight + bldguse +
                         f_baths + h_baths + fireplace_dum +  
                         garage_dum + bsmt_dum +
                         percent_vacant + zone_change + sale_z_old +
                         CN_score + Neighborhood + HIGH_SCH + 
                         dist_cityhall + dist_ugb + ", con_names))
MUpreanalysis_log.mod <- lm(MUpreanalysis_log, MUdat1)

summary(MUpreanalysis_log.mod)

# LOG REGRESSION LESS CRAZY --------------------------------------------

MUpreanalysis2_log = formula(paste0("SALEPRICElog ~ 
                          owner_state_dummy + age_sold + 
                         totalsqft +  taxlot_area + 
                         volume + FLOORS + UNITS + maxheight + bldguse +
                         garage_dum + bsmt_dum +
                         percent_vacant + zone_change +
                         CN_score + 
                         dist_cityhall + dist_ugb + ", con_names))
MUpreanalysis2_log.mod <- lm(MUpreanalysis2_log, MUdat1)

summary(MUpreanalysis2_log.mod)

```



# OUTPUT FILES IN HTML

```{r}

MUdat20 <- MUdat1 %>% # removed 78 obs
  filter(arms_length20 == TRUE)
MUbase100_log = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         percent_vacant + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names))
MUbase20_log.mod <- lm(MUbase20_log, MUdat20)
summary(MUbase20_log.mod)


### Regression 7: Mega Sexy Final Model
stargazer(
  MUbase20_log.mod, 
  type = "html",
  title = "Mixed-use Residential Results",
  style = "io",
  out = "MUmodels_finalsapp.htm",
  column.labels = c("Log Sale Price <br> (standard error)"),
  covariate.labels = c(
    "Constant",
    "Age When Sold", "Building Footprint Squared (sqft)", "Taxlot Area Squared (sqft)",
    "Number of Floors", "Maximum Building Height (ft)", "Buildnig Use Dummy", 
    "Full Baths", "Half Baths", "Vacant Properties in 200ft Radius (%)",
    "Zoning Dummy 1", "Zoning Dummy 2", "Zoning Dummy 3",
    "Complete Neighborhoods Score (0-100)",
    "Distance to Central Business District (ft)",
    "Distance to Urban Growth Boundary (ft)",
    
        "DEQ Environmental Cleanup Sites (ECSI)",
        "DEQ Leaking Underground Storage Tank Cleanup Sites (LUST)",
        "Historic and Conservation Districts",
        "Historic and Conservation Landmarks",
        "Areas Requiring Archeological Scan or Consultation with Tribes",
        "Conservation Zones",
        "Preservation Zones",
        "Approach and Departure Cones",
        "Helipad Landing",
        "Airport Noise",
        "Greenway",
        "DOGAMI Landslide Hazard Area",
        "DOGAMI Digital Landslide Database (SLIDO)",
        "FEMA 100-Year Floodplain Map",
        "Slopes Over 25% Incline",
        "Sewer System",
        "Stormwater System",
        "Water System",
        "Wetlands",
        "Institutional Campuses",
        "Private/Common Open Space",
        "Publicly Owned Lots",
        "Scenic Views",
        "Traffic Volume Exceeds Capacity",
        "ODOT Highway Interchanges",
        "Substandard and Unimproved Streets"), # rename labels
  initial.zero = TRUE,
  notes.align = "l",
  single.row = FALSE,
  keep.stat = c("n", "rsq"),
  no.space = TRUE,
  colnames = FALSE,
  digits.extra = 3,
  intercept.bottom = FALSE,
  header = FALSE)


MUbase20_log.mod <- data.frame(coef = MUbase20_log.mod[["coefficients"]]) %>%
  filter(is.na(coef) == FALSE) %>%
  mutate(interpretlog = exp(coef) - 1)
                             
interpretlog <- as.vector(MUbase20_log.mod$interpretlog)

plot(MUbase20_log.mod)
# remove ecsi, coverly, poverly, noise, gw, slido, JUST FOR VIF TEST
clean_vif <- MU %>%
  dplyr::select(conLUST, 
                conHist, conHistLdm,
                conAirHgt,
                conLSHA, conFld100, conSlp25, 
                conStorm, conWater,
                conTranSub)
clean_vif_names <- names(clean_vif)
con_names_vif <- paste(clean_vif_names, collapse = " + ")

# took out canopy cover and vacancy dummy
MUbase_log_vif = formula(paste0("SALEPRICElog ~ 
                             age_sold + totalsqft_sqd + taxlot_area_sqd + 
                         FLOORS + maxheight + bldguse + 
                         f_baths + h_baths + 
                         percent_vacant + sale_z_new + 
                         CN_score + dist_cityhall + dist_ugb + ", con_names_vif))

MUbase_log_vif.mod <- lm(MUbase_log_vif, MUdat1)
summary(MUbase_log_vif.mod)
alias(MUbase_log_vif.mod)
car::vif(MUbase_log_vif.mod, singular.ok = TRUE)


MUcons_table <- MUdat1 %>%
  dplyr::select(conECSI, conLUST, 
                conHist, conHistLdm, conNatAm,
                conCovrly, conPovrly,
                conAirHgt, conHeliprt, conNoise,
                conGW,
                conLSHA, conSLIDO, conFld100, conSlp25, 
                conSewer, conStorm, conWater,
                conWetland,
                conInstit, conPrvCom, conPubOwn,
                conView,
                conTranCap, conTranInt, conTranSub) %>%
  pivot_longer(cols = starts_with("con"),
               names_to = "Constraint",
               values_to = "Value") %>%
  group_by(Constraint, Value) %>%
  summarize(Count = n()) %>%
  pivot_wider(names_from = Value,
              values_from = Count) %>%
  rename(Yes = `1`,
         No = `0`) %>%
  mutate(Percent_Yes = (Yes/No)*100)

rawMUcons_table <- MU %>%
  dplyr::select(conECSI, conLUST, 
                conHist, conHistLdm, conNatAm,
                conCovrly, conPovrly,
                conAirHgt, conHeliprt, conNoise,
                conGW,
                conLSHA, conSLIDO, conFld100, conSlp25, 
                conSewer, conStorm, conWater,
                conWetland,
                conInstit, conPrvCom, conPubOwn,
                conView,
                conTranCap, conTranInt, conTranSub) %>%
  pivot_longer(cols = starts_with("con"),
               names_to = "Constraint",
               values_to = "Value") %>%
  group_by(Constraint, Value) %>%
  summarize(Count = n()) %>%
  pivot_wider(names_from = Value,
              values_from = Count) %>%
  rename(Yes = `1`,
         No = `0`) %>%
  mutate(Percent_Yes = (Yes/No)*100)

```