---
title: "Tables and Figures"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(here)
library(nlme)
```

# Load in cleaned data and define constraints + variables
```{r}
constraints <- c("conWetland", "conAirHgt",
                    "conCovrly", "conPovrly",
                   "conHist", "conHistLdm", 
                 "conLSHA", "conLUST",
                   "conNoise", "conSewer", "conPrvCom", "conSLIDO",
                   "conSlp25", "conStorm", "conTranCap", "conTranSub",
                   "conTranInt", "conTranSub", "conWater", 
                 "conGW", "conPubOwn", "conFld100_ft", "conECSI")

# ----------------------SFR------------------------------
sfr.dat <- read.csv(here("DATA", "sfr-cleaned.csv"))
sfr_vars <- c("dist_cityhall", "dist_ugb", "h_baths",
              "f_baths", "AREA", "maxheight", "totalsqft", "garage_dum","bsmt_dum",
              "pct_canopy_cov", "YEARBUILT", "n_fireplaces", "CN_score", "attic_dum", "year_sold", 
              "percent_vacant", "I(AREA^2)", "I(totalsqft^2)", "I(CN_score^2)")
collinearity.sfr <- c("conWetland", "conPrvCom")

# -----------------------MFR-----------------------------
mfr.dat <- read.csv(here("DATA", "mfr-cleaned.csv"))

mfr_vars <- c("dist_cityhall", "dist_ugb", "h_baths",
              "f_baths", "AREA", "maxheight", "garage_dum","bsmt_dum", 
              "pct_canopy_cov", "YEARBUILT", "CN_score", "attic_dum", "year_sold", "n_fireplaces",
              "percent_vacant", "n_units", "n_buildings", "totalsqft", "I(totalsqft^2)", "I(AREA^2)", "I(f_baths^2)")

collinearity.mfr <- c("conWetland", "conPrvCom", "conPovrly", "conSewer", "conLUST")
```

# Define functions
```{R}
# input: a vector of strings tht are the names of variables
# output: formula object with `lnprice` as dependent variable
genFormula <- function(...){
  string <- paste(c(...), collapse = " + ")
  paste0("lnprice ~", string) %>% as.formula
}

# cut out parts of the outreg table (to avoid spitting out coefs of the nbhds)
# outregChooseVars <- function(table, vars, withEndStats = T){
#   i <- table %>% pull(Variable) %in% vars %>% which
#   print(i)
#   indicies <- seq(from = i[1], to = i[length(i)] + 1)
#   if(withEndStats){
#     n <- nrow(table)
#     indicies <- c(indicies, (n-4):n)
#   }
#   table[indicies,]
# }

# remove transformations to variable names, output list of strings denoting
# variables used in lm fitting
pullVarname <- function(vars){
  sapply(vars, gsub, pattern = "\\(|\\)|I\\(|log|\\^2", replace = "") %>%
    unique()
}

# exchange code names for their descriptions in summary statistic tables
getDesc <- function(vars){
    crosswalk <- data.frame(Description = 
                              c("Number of half baths", "Number of full baths", 
            "Number of fireplaces", "Basement dummy",
            "Garage dummy", "Attic dummy", "Year sold", "Year property was built",
            "Percent canopy coverage", 
            "Percent of properties within a 200 ft. radius that are vacant",
            "Distance to nearest portion of urban growth boundary (ft.)",
            "Distance to city hall (ft.)", "Lot square footage", "Maximum building height (ft.)",
            "Total building square footage", "Imputed building square footage",
            "Complete Neighborhoods score",
            "Number of units", "Total building square footage", "Number of buildings within taxlot", "Number of units within taxlot"),
            
            Variable = c("h_baths", "f_baths", "n_fireplaces", 
         "bsmt_dum", "garage_dum", "attic_dum", 
         "year_sold", "YEARBUILT", 
         "pct_canopy_cov", "percent_vacant", 
         "dist_ugb", "dist_cityhall", "AREA", "maxheight", 
         "BLDGSQFT", "bldgsqft_imp", "CN_score", "UNITS", "totalsqft", "n_buildings",
         "n_units"))
    
    crosswalk %>% 
      filter(Variable %in% vars)
}

# make a pretty, customized summary table
summaryTable <- function(data, vars){
  stopifnot(is.data.frame(data))
  require(magrittr)
  require(purrr)
  data %<>%
  dplyr::select(pullVarname(vars)) %>%
    mutate_if(is.logical, ~.*1) %>%
    mutate(year_sold = as.numeric(year_sold))

  mean <- sapply(data, mean, na.rm = T)
  sd <- sapply(data, sd, na.rm = T)
  median <- sapply(data, median, na.rm = T)
  max <- sapply(data, max, na.rm = T)
  min <- sapply(data, min, na.rm = T)
  data.frame(Variable = colnames(data),
            Mean = mean,
            St.Dev. = sd,
             Median = median,
             Min = min,
             Max = max) %>%
    left_join(pullVarname(vars) %>% getDesc(), by = "Variable") %>%
    mutate(Min = round(Min, 3),
           Mean = ifelse(Variable %in% c('YEARBUILT',"year_sold"),
                         floor(Mean), Mean)) %>%
    mutate_if(is.numeric, ~round(., digits = 3) %>%
                format(., trim = T, digits = 3, 
                                  width = 5, scientific = F,
                                  drop0trailing = T)) %>%
    dplyr::select(Variable, Description, everything()) %>%
    mutate(Variable = tolower(Variable))
}

# round_df <- function(x, digits) {
#   # round all numeric variables
#   # x: data frame 
#   # digits: number of digits to round
#   numeric_columns <- sapply(x, mode) == 'numeric'
#   x[numeric_columns] <-  round(x[numeric_columns], digits)
#   x
# }

# pretty <- function(table, full = T){
#   table %>%
#   kable("latex", booktabs = T, row.names = F) %>%
#   kable_styling(full_width = full) %>%
#     column_spec(column = 1, width_min = "3cm")
# }

# To estimate all 6 models at once using various data and variables, 
# outputs the results of the fits in a list of model objects
estimateModels <- function(data, variables, dist.vars = "", collin = ""){

  constraints <- setdiff(constraints, collin) # depending on property type some constraints
  # were collinear
  
  controls <- lm(genFormula(variables), data)
  nbhd <- lm(genFormula(setdiff(variables, dist.vars), "nbhd"), 
                   data)
  const <- lm(genFormula(variables, constraints), 
                   data = data)
  const.nbhd <- lm(genFormula(setdiff(variables, dist.vars), constraints, "nbhd"), 
                         data = data)
  quad <- lm(genFormula(variables, "sextant"), 
                         data = data)
  const.quad <- lm(genFormula(variables, constraints, "sextant"), 
                         data = data)
  list(controls, quad, nbhd, const, const.quad, const.nbhd)
}


# makeSARtbl <- function(x){
#   summary(x)$Coef %>%
#   as.data.frame %>%
#   rownames_to_column(var = "Variable")
# }

# addBrackets <- function(x){
#   left <-  paste0("[", x)
#   paste0(left, "]")
# }

# getSE <- function(table){
#  table %<>% dplyr::select(matches("error"), Variable, matches("Value|Estimate")) %>%
#     dplyr::select(-matches("z|-"))
#  error.name <- colnames(table)[1]
#  estimate.name <- colnames(table)[3]
#  table %>% pivot_longer(cols = c(error.name, estimate.name), 
#                    names_to = "Statistic", values_to = "Value") %>%
#    round_df(3) %>%
#    mutate(Value = ifelse(Statistic == error.name, addBrackets(Value), Value),
#           Statistic = ifelse(Statistic == error.name, "Std Err", "Estimate"))
# }

# table_join <- function(output, input, colname){
#   varcol <- output[["Variable"]]
#   orig <- varcol
#   for(i in 2:length(varcol)){
#     if(varcol[i] == "" & varcol[i - 1] != ""){
#       varcol[i] <- varcol[i - 1]}
#   }
#   varcol[(length(varcol)-3):length(varcol)] <- ""
#   output %>%
#     mutate(Variable = varcol) %>%
#     left_join(getSE(input), by = c("Variable", "Statistic")) %>%
#     mutate(Variable = orig) %>%
#     dplyr::rename_(.dots = setNames("Value", colname))
# }

# stylized modification of the stargazer function, to avoid lotsa repeated code
my_reg_table  <- function(models = ..., title = "", omit, column.labels, 
                          fname, digits = 5){
  stargazer(models,
          type = "html",
          style = "aer",
          title = title,
          out = here("Ryan", "figs", "tables", "html-tables",
                     fname), 
          summary = F,
          column.labels = column.labels,
          dep.var.labels.include = FALSE,
          model.names = FALSE,
          omit = omit, 
          digits = digits,
          star.cutoffs = c(0.05, 0.01)
          )
}
```

* * *

# Tables
**Workflow**:

1) The function `stargazer()` from package of the same name takes an input data.frame produced by my function `summaryTable()` and outputs the data frame in a nicely formatted html table. 

2) The tables are opened in a web browser (Chrome) and copied into the thesis Word document.

The tables produced below are saved in the github directory: Thesis/Ryan/figs/tables/html-tables. I use stargazer for ease of transferring into Word.

## Constraint counts table (table 6)
```{r}
mfr.counts <- mfr.dat %>% select(matches("con")) %>%
  colSums()

sfr.counts <- sfr.dat %>% select(matches("con")) %>%
  colSums()
counts.tbl <- data.frame(sfr.counts, mfr.counts) 
colnames(counts.tbl) <- c("SFR", "MFR")

# export counts table to html file with stargazer
stargazer(counts.tbl, type = "html",
          title = "Number of Properties within Constraints",
          style = "io",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "const-counts.htm"),
          column.labels = c("SFR", "MFR"),
          summary = F)
```

## Summary stats tables (tables 4, 5, 3)
```{R}
# write sfr summary table to html file
stargazer(summaryTable(sfr.dat, sfr_vars) %>% select(-Variable),
          type = "html",
          style = "aer",
          title = "Single-family Residential Summary Statistics",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "sfr-sum-stats.htm"), 
          summary = F,
          rownames = F)

# write mfr... "" 
stargazer(summaryTable(mfr.dat, mfr_vars) %>% select(-Variable),
          type = "html",
          style = "aer",
          title = "Multi-family Residential Summary Statistics",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "mfr-sum-stats.htm"), 
          summary = F,
          rownames = F)

saleprice <- data.frame(Type = c(rep("SFR", nrow(sfr.dat)), rep("MFR", nrow(mfr.dat))),
                 `SFR Sale Price` = c(exp(sfr.dat$lnprice), 
                           rep(NA, nrow(mfr.dat))),
                 `MFR Sale Price` = c(exp(mfr.dat$lnprice), 
                           rep(NA, nrow(sfr.dat))))

# write dependent variable summary stats by property type (MFR & SFR) to html
saleprice %>%
stargazer(type = 'html',
          digits = 0,
           style = "aer",
          title = "Sale Price Summary Statistics",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "price-sum-stats.htm"))
```

## VIF tables (not included)
Note that these tables don't appear in the body of the thesis document, but were used to diagnose multicollinearity problems and discussed in my Results and Model Diagnostics sections.

They are saved with the rest of the tables in the folder html-tables.
```{R}
# single 
car::vif(mfr_mods[[6]]) %>% as.data.frame() %>% rownames_to_column() %>%
  arrange(desc(GVIF))

# VIF table of MFR neighborhood level fixed effects model
car::vif(mfr_mods[[6]]) %>% as.data.frame() %>% rownames_to_column() %>%
  arrange(desc(GVIF)) %>% head() %>%
  stargazer(
          type = "html",
          style = "aer",
          title = "Multi-family Residential VIF",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "mfr-vif.htm"), 
          summary = F,
          rownames = F)

# VIF table of variables within the quadrant level fixed effects model
car::vif(mfr_mods[[5]]) %>% as.data.frame() %>% rownames_to_column() %>%
  arrange(desc(GVIF))  %>%
  stargazer(
          type = "html",
          style = "aer",
          title = "Multi-family Residential VIF",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "mfr-vif-quad.htm"), 
          summary = F,
          rownames = F)

# VIF table of the full SFR neighborhood level fixed effects model
car::vif(sfr_mods[[6]]) %>% as.data.frame() %>% rownames_to_column() %>%
  arrange(desc(GVIF)) %>% slice(1:20) %>%
  stargazer(
          type = "html",
          style = "aer",
          title = "Single-family Residential VIF",
          out = here("Ryan", "figs", "tables", "html-tables",
                     "sfr-vif.htm"), 
          summary = F,
          rownames = F)
```

* * *

## Regression tables
**Workflow:**

1) Use my function `estimateModels()` to create 6 semi-log models based on a fixed set of control variables and various levels of fixed effects/spatial dummies: none, quadrant-, and neighborhood-level. Save models in a list `sfr_mods`. 

2) Fit random effects model, random intercepts at the neighborhood level, using the `lme()` (linear mixed effects) function from the package `nlme`. This outputs an object of class `lme` that works nicely with stargazer. 

3) Save the random effects model as the 7th element in `sfr_mods`

4) Repeat 1-2 for MFR, in list of model objects, `mfr_mods`. End up with 7 SFR models and 6 MFR models.

5) Use function `my_reg_table()`, my variant of `stargazer()` with specific formatting options selected (i.e. star/significance levels, heading labels, etc) to avoid copy pasting long sections of code. Export 3 html tables for each property type: coefficients of control variables, constraint variables, and full regression results.


### SFR (tables 7, 8, B.1)
```{r}
model_labels <- c("Baseline", "Quadrant FE", "Neighborhood FE", 
                       "Baseline + constraints", "Quadrant FE + constraints", 
                  "Neighborhood FE + constraints", "Neighborhood RE + constraints")

# estimate all 6 SFR models
sfr_mods <- estimateModels(sfr.dat, sfr_vars, 
                           collin = collinearity.sfr)

# -----------------------------------
# fit re model
re_sfr <- lme(genFormula(sfr_vars, dplyr::setdiff(constraints, collinearity.sfr)), 
          random = ~ 1|nbhd,
            data=sfr.dat,
            method="REML")  

sfr_mods[[7]] <- re_sfr
# -----------------------------------

# EXPORT SFR REGRESSION TABLES 
# control vars
my_reg_table(sfr_mods, title = "SFR Results: Controls", 
             omit = c("nbhd", "sextant", constraints), column.labels = model_labels, 
                          "sfr-results-controls.htm", digits = 5)

# constraint vars
my_reg_table(sfr_mods[4:7], title = "SFR Results: Constraints",
             omit = c("nbhd", "sextant", sfr_vars), column.labels = model_labels[1:4],
             "sfr-results-constraints.htm", digits = 5)
          
# all vars (including neighborhood/quadrant FE)
my_reg_table(sfr_mods, title = "Single-family Residential Full Results",
             omit = NULL, column.labels = model_labels,
             "sfr-full-results.htm", digits = 5)          
```

### MFR (tables 9, 10, B.2)
```{r}
mfr_mods <- estimateModels(mfr.dat, mfr_vars, 
                           collin = collinearity.mfr)

# fit re model
re_mfr <- lme(genFormula(mfr_vars, dplyr::setdiff(constraints, collinearity.mfr)), 
          random = ~ 1|nbhd,
            data=mfr.dat,
            method="REML")  

mfr_mods[[7]] <- re_mfr
                    
# EXPORT MFR REGRESSION TABLES 
# control vars
my_reg_table(mfr_mods, title = "MFR Results: Controls",
             column.labels = model_labels,
             omit = c("nbhd", "sextant", constraints),
             fname = "mfr-results-controls.htm")

# constraint vars
my_reg_table(mfr_mods[4:7], title = "MFR Results: Constraints",
             column.labels = c(model_labels[1:3], 
                               "Neighborhood RE"),
             omit = c("nbhd", "sextant", mfr_vars),
             fname = "mfr-results-constraints.htm")

# all vars
my_reg_table(mfr_mods, title = "MFR Full Results",
             omit = NULL, column.labels = model_labels,
             fname = "mfr-full-results.htm")
```

\newpage

# Constructing Figures
The figures below are included in the thesis document.

## QQ-plots of best SFR and MFR model (fig 11)
```{R}
# single
plot(sfr_mods[[6]], 2, sub.caption = NA, 
     caption = rep("SFR FE model (6): Normal Q-Q", 6)) 

# multi
plot(mfr_mods[[5]], 2, sub.caption = NA,
     caption = rep("MFR FE model (6): Normal Q-Q", 6))
```

## Distribution of Sale Price (fig 8)
```{R}
ggplot(sfr.dat, aes(lnprice)) + geom_histogram() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "grey92")) + 
  labs(x = "Log of sale price", y = "",
       title = "SFR Distribution of Logged Sale Price")
ggsave(here("Ryan", "figs", "plots", "sfr-totsqft.png"))


ggplot(mfr.dat, aes(lnprice)) + geom_histogram() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "grey92")) + 
  labs(x = "Log of sale price", y = "",
       title = "MFR Distribution of Logged Sale Price")
ggsave(here("Ryan", "figs", "plots", "sfr-totsqft.png"))

```

## SFR non-linearity scatterplots (figs 6, 10)
```{r}
# sfr totalsqft, quadratic relationship
ggplot(sfr.dat, aes(totalsqft, lnprice)) + geom_point() + geom_smooth() +
    labs(x = "Total building square footage", title = "SFR") +
  theme_minimal()
ggsave(here("Ryan", "figs", "plots", "sfr-totsqft.png"))

# mfr totalsqft, quadratic relationship
ggplot(mfr.dat, aes(totalsqft, lnprice)) + geom_point() + xlim(0, 40000) +
  geom_smooth() + 
  labs(x = "Total building square footage", title = "MFR") + 
  theme_minimal()
ggsave(here("Ryan", "figs", "plots", "mfr-totsqft.png"))

# sfr cn_score, quadratic relationship
ggplot(sfr.dat, aes(CN_score, lnprice)) + geom_jitter() + geom_smooth() + 
    labs(x = "Complete Neighborhoods Score", title = "SFR") +
  theme_minimal()
ggsave(here("Ryan", "figs", "plots", "sfr-cnscore.png"))

# mfr cn_score, linear relationship
ggplot(mfr.dat, aes(CN_score, lnprice)) + geom_jitter() +
  geom_smooth() + theme_minimal() +
  labs(x = "Complete Neighborhoods Score", title = "MFR")
ggsave(here("Ryan", "figs", "plots", "mfr-cnscore.png"))

```

## MFR building squarefootage imputation scatterplot (not included)
```{R}
ggplot(mfr.dat, aes(bldgsqft_imp, lnprice, color = imputed)) + 
  geom_point(alpha = .5) +
  scale_color_discrete(name = "Imputed from", 
                       labels = c("taxlots", "building footprints")) +
  xlim(0, 5000) +
  labs(x = "Building square footage", y = "Log of sale price") +
  theme_minimal() %>%
ggsave(here("Ryan", "figs", "plots", "mfr-bldg-imp.png"))

```

# MAPS
Not used. Tried to get a basemap but then ditched it. Kept here because the code could be useful once I figure out how to use the Google API. 

```{R}
# devtools::install_github("dkahle/ggmap")
# library(ggmap)
# 
# register_google(key = "AIzaSyAOOHL4IjiMZlaXD7R7IKiDrNes8KNfoOo")
# has_google_key()
# ggmap(get_googlemap())
# base_map <- get_map(location = c(lon = 122.67, lat = 40.5))
```


