---
title: "Tables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(here)
library(kableExtra)
```

# set up full data frame
```{r}
#df <- read.csv(here("thesis_data3-7.csv"))

constraints <- c("conWetland", "conAirHgt",
                    "conCovrly", "conPovrly",
                   "conHist", "conHistLdm", 
                 "conLSHA", "conLUST",
                   "conNoise", "conPrvCom", "conSewer", "conSLIDO",
                   "conSlp25", "conStorm", "conTranCap", "conTranSub",
                   "conTranInt", "conTranSub", "conWater", 
                 "conGW", "conPubOwn", "conFld100_ft", "conECSI")
# define helper function to switch NAs in the constraints to 0s
to0 <- function(x){ifelse(is.na(x), 0, x)}
# 
# 
# # CREATE FLAG & ARMS LENGTH VARIABLES
# df %<>%
#   rename(nbhd = NAME) %>%
#   mutate(n_fireplaces = ifelse(is.na(n_fireplaces), 0, n_fireplaces), 
#          saledate = as.Date(saledate),
#          lnprice = log(SALEPRICE),
#          
#          # define flags
#          proud_flag =  grepl("PROUD", OWNER1) | 
#            grepl("PROUD", OWNER2) | grepl("PROUD", OWNER3),
#          trust_flag = grepl("TRUST", OWNER1) | 
#            grepl("TRUST", OWNER2) | grepl("TRUST", OWNER3), 
#          top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
#          price_diff = SALEPRICE - LANDVAL3, 
#          price_ratio = SALEPRICE/LANDVAL3 * 100,
#          vacant_dummy = PRPCD_DESC == "VACANT LAND",
#          
#          #make percentages
#          pct_canopy_cov = 100*pct_canopy_cov,
#          percent_vacant = 100*percent_vacant)
#------------------------- 

df <- read.csv(here("DATA", "thesis-data_4-5.csv"))

# MAKE DROPS
trim <- df %>% 
  filter(proud_flag == F, top_1 == F,
           price_ratio > 100, vacant_dummy == F) %>%
  mutate_at(vars(constraints), to0) %>%
  mutate(YEARBUILT = as.numeric(YEARBUILT)) %>%
  mutate(YEARBUILT = case_when(
    YEARBUILT < 1000 ~ NA_real_,
    YEARBUILT > 2019 ~ NA_real_,
    TRUE ~ YEARBUILT))

constraint_sums <- trim %>%
  select(constraints) %>%
  rowSums()

trim <- trim %>%
  mutate(is_constrained = constraint_sums > 0)

# ---------------
# SQUARE FOOTAGE VARIABLES
# garage sqft
gar_sqft_sum <- trim %>%
  select(matches("gar")) %>%
  rowSums()

# attic sqft
attic_sqft_sum <- trim %>%
  select(matches("attic")) %>%
  rowSums()

# basement sqft
bsmt_sqft_sum <- trim %>%
  select(matches("bsmt")) %>%
  select(-c("BSMT.PARKING","BSMT.GAR")) %>%
  rowSums()

# define dummies
trim <- trim %>%
  mutate(garage_sqft = gar_sqft_sum,
         garage_dum = garage_sqft > 0,
         attic_sqft = attic_sqft_sum,
         attic_dum = attic_sqft > 0,
         bsmt_sqft = bsmt_sqft_sum,
         bsmt_dum = bsmt_sqft > 0,
         year_sold = format(as.Date(saledate), "%Y"))
         


# ---------------
```

## clean MFR
```{r, cache = F,  include=FALSE}
mfr.dat <- trim %>%
  filter(prop_type == "Multi-family")

# how many missing fireplaces?
mfr.dat %>% filter(is.na(n_fireplaces)) %>% count

mfr.dat %<>%
  filter(!(is.na(totalsqft) & BLDGSQFT == 0),
         AREA < 100000) %>%
  mutate(bldgsqft_imp = case_when(is.na(totalsqft) ~ BLDGSQFT,
                                  BLDGSQFT == 0 ~ totalsqft,
                                  TRUE ~ BLDGSQFT),
         imputed = is.na(totalsqft)) 
        # dist_cityhall = dist_cityhall/1000,
        # dist_ugb = dist_ugb / 1000,
        # AREA = AREA / 100,
         # bldgsqft_imp = bldgsqft_imp / 100)

# define outliers (these keep changing as i change outlier definitions above
# should use stateid insteadddd)
mfr.outliers <- c(849, 1186)
funkypts <- c(4182, 2839, 4189, 1137, 713, 459, 1893)
```

## clean SFR
```{r, cache = T,  include=FALSE}
sfr.dat <- trim %>%
  filter(prop_type == "Single-family")
dim(sfr.dat)
sfr.dat %<>%
  mutate(empty_lot_flag = BLDGSQFT == 0, is.na(totalsqft),
         maybe_mfr_flag = UNITS > 5 | f_baths > 10,
         big_sqft_flag = BLDGSQFT > 10000,
         big_bsmt_flag = bsmt_sqft > 9000,
         big_area_flag = AREA > 100000) %>%
        # dist_ugb = dist_ugb / 1000,
        # AREA = AREA / 100,
        # BLDGSQFT = BLDGSQFT/100) %>%
    filter(empty_lot_flag == F,
         maybe_mfr_flag == F, 
         big_area_flag == F,
         big_sqft_flag == F,
         price_ratio > 100)
```


### define pretty formula and table helper functions
```{r, cache = T,  include=FALSE}
# input a vector of strings tht are the names of variables
genFormula <- function(...){
  string <- paste(c(...), collapse = " + ")
  paste0("lnprice ~", string) %>% as.formula
}

# cut out parts of the outreg table (to avoid spitting out coefs of the nbhds)
outregChooseVars <- function(table, vars, withEndStats = T){
  i <- table %>% pull(Variable) %in% vars %>% which
  print(i)
  indicies <- seq(from = i[1], to = i[length(i)] + 1)
  if(withEndStats){
    n <- nrow(table)
    indicies <- c(indicies, (n-4):n)
  }
  table[indicies,]
}
```


# ~~MFR~~ 

## MFR: define control variables and estimate models
```{r, cache = T,  include=FALSE}
mfr_vars <- c("I(log(dist_cityhall))", "I(log(dist_ugb))", "h_baths",
"f_baths", "AREA", "avgheight", "garage_dum","bsmt_dum",
"pct_canopy_cov", "YEARBUILT", "CN_score", "attic_dum", "year_sold", "n_fireplaces",
"percent_vacant", "UNITS", "bldgsqft_imp", "I(bldgsqft_imp^2)", "I(AREA^2)", "I(f_baths^2)")


m1.mf <- lm(genFormula(mfr_vars), mfr.dat[-funkypts,])
m2.nbhd.mf <- lm(genFormula(mfr_vars, "nbhd"), 
                 mfr.dat[-funkypts,])
m3.const.mf <- lm(genFormula(mfr_vars, constraints), 
                  data = mfr.dat[-funkypts,])
m4.const.nbhd.mf <- lm(genFormula(mfr_vars, constraints, "nbhd"), 
                       data = mfr.dat[-funkypts,])
plot(m4.const.nbhd.mf)
```

## MFR: write models to table using outreg package
```{r echo=FALSE, eval=F, include = F}
mfr.table <- outreg::outreg(list(m3.const.mf, m1.mf, m4.const.nbhd.mf, m2.nbhd.mf), 
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE) %>%
    rename(Stat = .stat) %>%
    mutate(Stat = ifelse(Stat %in% c("Estimate", "Std Err"), "", Stat))


colnames(mfr.table) <- c("Variable", "Statistic",
                               "No Spatial Dummies, Constraints", 
                         "No Spatial Dummies, No Constraints",
                         "Spatial Dummies, Constraints",
                         "Spatial Dummies, No Constraints")


mfr.controls <- outregChooseVars(mfr.table, mfr_vars)
mfr.constraints <-  outregChooseVars(mfr.table, constraints) %>%
  select(-matches("no constraints"))

mfr.constraints %>%
  kable("latex", booktabs = T, row.names = F,
        label = "MFR Controls Regression") %>% 
  kable_styling(full_width = F)

mfr.controls %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)
```


# ~SFR~

## SFR: define control variables and estimate models
```{r cache=T}
sfr_vars <- c("I(log(dist_cityhall))", "I(log(dist_ugb))", "h_baths",
"f_baths", "AREA", "avgheight", "BLDGSQFT", "garage_dum","bsmt_dum",
"pct_canopy_cov", "YEARBUILT", "n_fireplaces", "CN_score", "attic_dum", "year_sold",
"percent_vacant", "I(AREA^2)", "I(BLDGSQFT^2)", "I(CN_score^2)")

# m1.sf <- lm(genFormula("is_constrained", sfr_vars), data = sfr.dat)
# m2.nbhd.sf <- lm(genFormula("is_constrained", sfr_vars, "nbhd"), data = sfr.dat)
# m3.const.sf <- lm(genFormula(sfr_vars, constraints), data = sfr.dat)
# m4.const.nbhd.sf <- lm(genFormula(sfr_vars, constraints, "nbhd"), data = sfr.dat)
# plot(m4.const.nbhd.sf)
```

## SFR: write regression output using outreg
```{r, eval = F, include=F}
# use robust standard errors
sfr.table <- outreg::outreg(list(m3.const.sf, m1.sf, m4.const.nbhd.sf, m2.nbhd.sf),
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE) %>%
  mutate(Stat = ifelse(.stat %in% c("Estimate", "Std Err"), "", .stat)) %>%
  select(-7)

colnames(sfr.table) <- c("Variable", "Statistic", 
                               "No Spatial Dummies, Constraints", 
                         "No Spatial Dummies, No Constraints",
                         "Spatial Dummies, Constraints",
                         "Spatial Dummies, No Constraints")

# grab the controls from outreg, get rid of stat column bc not presenting
# r sq with the controls
sfr.controls <- outregChooseVars(sfr.table, sfr_vars, withEndStats = F) %>%
  select(-c(Statistic))

# grab only the constraints from outreg output
sfr.constraints <- outregChooseVars(sfr.table, constraints) %>%
  select(-matches("no constraints"))

# write.csv(sfr.constraints, here::here("Ryan", "figs", "tables",
#                                       "sfr-constraints.csv"))

# produce 4 model tables for SFR constraints...
sfr.constraints %>%
  kable("latex", booktabs = T, row.names = F,
        caption = "SFR Constraints Regression") %>% 
  kable_styling(full_width = F)

#... and controls
sfr.controls %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)
```

# sum stats

```{r, eval = F}
n_mfr_constraints <- mfr.dat %>%
  select(matches("con")) %>%
  select_if(is.numeric) %>%
  select(-contains("pct")) %>% colSums(na.rm = T)

n_sfr_constraints <- sfr.dat %>%
  select(matches("con")) %>%
  select_if(is.numeric) %>%
  select(-contains("pct")) %>% colSums(na.rm = T)

sfr.con <- sfr.dat %>%
  select(matches("con")) %>%
  select_if(is.numeric) %>%
  select(-contains("pct")) 
constraints <- sfr.con %>% colnames

# constraint counts
data.frame(Constraint = c(constraints),
           SFR = n_sfr_constraints, 
           MFR = n_mfr_constraints) %>%
    kable("latex", booktabs = T, row.names = F, 
          caption = "Constraint Counts") %>% 
  kable_styling(full_width = F)
```


# cts vars sum stats
Pretty summary stats table function. It produces a data.frame/tibble that can be wrapped in kable/kableExtra, written to an excel file, etc. 

```{r}
pullVarname <- function(vars){
  sapply(vars, gsub, pattern = "\\(|\\)|I\\(|log|\\^2", replace = "") %>%
    unique()
}

getDesc <- function(vars){
    crosswalk <- data.frame(desc = c("Number of half baths", "Number of full baths", 
            "Number of fireplaces", "Basement dummy",
            "Garage dummy", "Attic dummy", "Year sold", "Year property was built",
            "Percent canopy coverage", 
            "Percent of properties within a \n 200 ft. radius that are vacant",
            "Distance to nearest portion \n of urban growth boundary",
            "Distance to city hall", "Lot square footage", "Average building height",
            "Total building square footage", "Imputed building square footage",
            "Complete Neighborhoods score",
            "Number of units"),
            
            var = c("h_baths", "f_baths", "n_fireplaces", 
         "bsmt_dum", "garage_dum", "attic_dum", 
         "year_sold", "YEARBUILT", 
         "pct_canopy_cov", "percent_vacant", 
         "dist_ugb", "dist_cityhall", "AREA", "avgheight", 
         "BLDGSQFT", "bldgsqft_imp", "CN_score", "UNITS"))
    
    crosswalk %>% filter(var %in% vars) %>% pull(desc)
}

summaryTable <- function(data, vars){
  stopifnot(is.data.frame(data))
  require(magrittr)
  require(purrr)
  data %<>%
  select(vars[vars %in% colnames(data)], dist_cityhall, dist_ugb) %>%
  select("h_baths", "f_baths", "n_fireplaces", 
         "bsmt_dum", "garage_dum", "attic_dum", 
         "year_sold", "YEARBUILT", 
         "pct_canopy_cov", "percent_vacant", 
         "dist_ugb", "dist_cityhall", everything()) %>%
    mutate_if(is.logical, ~.*1) %>%
    mutate(year_sold = as.numeric(year_sold))
  
  mean <- sapply(data, mean, na.rm = T)
  sd <- sapply(data, sd, na.rm = T)
  median <- sapply(data, median, na.rm = T)
  max <- sapply(data, max, na.rm = T)
  min <- sapply(data, min, na.rm = T)
  data.frame(Statistic = colnames(data),
             Description = colnames(data) %>% getDesc(),
            Mean = mean,
            St.Dev. = sd,
             Median = median,
             Min = min,
             Max = max) %>%
    mutate(Min = round(Min, 3),
           Mean = ifelse(Statistic %in% c('YEARBUILT',"year_sold"),
                         floor(Mean), Mean)) %>%
    mutate_if(is.numeric, ~round(., digits = 3) %>%
                format(., trim = T, digits = 3, 
                                  width = 5, scientific = F,
                                  drop0trailing = T))
}

# sfr sum stats
summaryTable(sfr.dat, sfr_vars) %>%
  kable("latex", booktabs = T, row.names = F) %>%
  kable_styling(full_width = T)

#mfr sum stats
summaryTable(mfr.dat, mfr_vars) %>%
  kable %>%
  kable_styling(full_width = F)

```


# sum stat independent variable: prices
Grouped summary stats

```{r echo=FALSE, eval=F, include = F}
df <- bind_rows(mfr.dat, sfr.dat)

m.price.stats <- df %>% filter(prop_type == "Multi-family") %>%
  pull(SALEPRICE) %>% summary()

s.price.stats <- sfr.dat %>%
  pull(SALEPRICE) %>% summary()

bind_rows(s.price.stats, m.price.stats) %>%
  mutate("Property Type" = c("SFR", "MFR")) %>%
  select("Property Type", everything()) %>%
  kable() %>%
  # kable("latex", booktabs = T, row.names = F,
  #       caption = "") %>%
  kable_styling(full_width = F)
```


# plots
These were plotted then saved into the plots folder, not running this here...
```{r}

```

# non linearities
```{r}


```

# mfr constraints
```{r, eval = F}
mfr.constraints %>%
  kable("latex", booktabs = T, row.names = F,
        label = "MFR Controls Regression") %>% 
  kable_styling(full_width = F)
```

# robustness function 
(so I change input data & reestimate the 4 models quickly)

```{r}
estimateModels <- function(data, variables){
  controls <- lm(genFormula(variables), data)
  nbhd <- lm(genFormula(variables, "nbhd"), 
                   data)
  const <- lm(genFormula(variables, constraints), 
                   data = data)
  const.nbhd <- lm(genFormula(variables, constraints, "nbhd"), 
                         data = data)
  quad <- lm(genFormula(variables, "sextant"), 
                         data = data)
  const.quad <- lm(genFormula(variables, constraints, "sextant"), 
                         data = data)
  list(controls, quad, nbhd, const, const.quad, const.nbhd)
}

```


# SFR: regression table, latex style: single, quadrants, nbhd
```{r}
sfr_mods <- estimateModels(sfr.dat, sfr_vars)
sfr_tbl <- outreg::outreg(sfr_mods,
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE)

colnames(sfr_tbl) <- c("Variable", "Statistic",
                       "Base controls", "Quadrant", "Nbhd", 
                       "Base constraints", "Constraints + quadrant", 
                       "Constraints + nbhd")

outregChooseVars(sfr_tbl, constraints) %>%
  select(Variable, Statistic, matches("Constraints")) %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)

outregChooseVars(sfr_tbl, sfr_vars, F) %>%
  select(-Statistic) %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)
```

# MFR: regression table, latex style: single, quadrants, nbhd
```{r}
mfr_mods <- estimateModels(mfr.dat, mfr_vars)
mfr_tbl <- outreg::outreg(mfr_mods,
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE)

colnames(sfr_tbl) <- c("Variable", "Statistic",
                       "Base controls", "Quadrant", "Nbhd", 
                       "Base constraints", "Constraints + quadrant", 
                       "Constraints + nbhd")

outregChooseVars(mfr_tbl, constraints) %>%
  select(Variable, Statistic, matches("Constraints")) %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)

outregChooseVars(mfr_tbl, mfr_vars, F) %>%
  select(-Statistic) %>%
  kable("latex", booktabs = T, row.names = F) %>% 
  kable_styling(full_width = T)
```

# export one big happy regression table
```{r, eval = F}
fname <- here("Ryan", "figs", "tables", "big-table.xlsx")

with_outliers_tbl <- outreg::outreg(c(sfr_w_outliers, mfr_w_outliers), 
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE)

colnames(with_outliers_tbl) <- c("Variable", "Statistic",
                               "SFR: No Dummies, No Constraints", 
                         "SFR: Dummies, No Constraints",
                         "SFR: No Dummies, Constraints",
                         "SFR: Spatial Dummies, Constraints",
                         "MFR: No Dummies, No Constraints", 
                         "MFR: Dummies, No Constraints",
                         "MFR: No Dummies, Constraints",
                         "MFR: Spatial Dummies, Constraints")

no_outliers_tbl <- outreg::outreg(c(mfr_no_outliers), 
               digits = 5L, alpha = c(0.05, 0.01),
       bracket = c("se"), starred = c("coef"), robust = TRUE, small = F,
       constlast = TRUE, norepeat = TRUE)

colnames(no_outliers_tbl) <- c("Variable", "Statistic",
                               "MFR: No Dummies, No Constraints", 
                         "MFR: Dummies, No Constraints",
                         "MFR: No Dummies, Constraints",
                         "MFR: Spatial Dummies, Constraints")

# export to xl
xlsx::write.xlsx(with_outliers_tbl, fname,
                 sheetName = "Outliers2", append = TRUE)

xlsx::write.xlsx(no_outliers_tbl, fname,
                 sheetName = "No Outliers2", append = TRUE)
```

