---
title: "Regressions"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
```{r include=FALSE}
library(tidyverse)
library(magrittr)
library(kableExtra)
library(caret)
```

## Load data and clean
1) Drop observations with ProudGround as the owner (unreliable sale prices). Define an "arms-length transaction" to be the ratio between the assessed land value and the sale price. Usually sale price is greater than the most recent assessed land value without improvements. I remove observations in which this ratio is less than .2, a more conservative approach. Note the median here is 220 and first quantile is 179.8.


```{r warning=FALSE}
df <- read_csv("/Users/ryankobler/Desktop/thesis/Thesis/DATA/thesis-data.csv")

# DROPS
df %<>%
  mutate(proud_flag =  grepl("PROUD", OWNER1) | grepl("PROUD", OWNER2) | grepl("PROUD", OWNER3),
         trust_flag = grepl("TRUST", OWNER1) | grepl("TRUST", OWNER2) | grepl("TRUST", OWNER3), 
         top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
         price_diff = SALEPRICE - LANDVAL3, 
         price_ratio = SALEPRICE/LANDVAL3 * 100,
         vacant_dummy = PRPCD_DESC == "VACANT LAND") %>%
  mutate(arms_length = price_ratio > 20)

constraints <- c("conWetland", "conNatAm", 
                   "conAirHgt", "conCovrly", "conPovrly", "conHeliprt",
                   "conHist", "conHistLdm", "conInstit", "conLSHA", "conLUST",
                   "conNoise", "conPrvCom", "conSewer", "conSLIDO",
                   "conSlp25", "conStorm", "conTranCap", "conTranSub",
                   "conTranInt", "conTranSub", "conView", "conWater", 
                 "conGW", "conPubOwn", "conFldway", "conFld100", "conECSI")
constraints.form <- paste(constraints, collapse = " + ")

# switch the NAs in the constraints to 0s
to0 <- function(x){ifelse(is.na(x), 0, x)}

trim <- df %>% 
  filter(proud_flag == F & top_1 == F & arms_length == T & vacant_dummy == F) %>%
  mutate_at(vars(constraints), to0) 

constraint_sums <- trim %>%
  select(constraints) %>%
  rowSums()

trim %<>%
  mutate(is_constrained = constraint_sums > 0)
```


## Regression 1
Without neighborhood or school catchment area fixed effects. 

```{r}
gar_sqft_sum <- trim %>%
  select(matches("gar")) %>%
  rowSums()

# attic sqft
attic_sqft_sum <- trim %>%
  select(matches("attic")) %>%
  rowSums()

trim %<>%
  mutate(garage_sqft = gar_sqft_sum,
         garage_dum = garage_sqft > 0,
         attic_sqft = attic_sqft_sum,
         attic_dum = attic_sqft > 0,
         year_sold = as.factor(format(saledate, "%Y")))
         
# since the date objects are all the same length, we can
# just gra

# 1. What units are avgheight in?
# 2. Do we have reliable number of stories
# 3. Recall that isVacant is the old guy/
formula_sfr <- as.formula(paste("I(log(SALEPRICE)) ~ h_baths + f_baths + n_fireplaces +
     pct_canopy_cov + dist_ugb + 
     dist_cityhall + YEARBUILT + CN_score + BLDGSQFT + 
     AREA + garage_sqft + attic_dum + avgheight + year_sold + ",
                            constraints.form))

m1 <- lm(formula_sfr, data = trim %>% filter(prop_type == "Single-family"))
summary(m1) 

formula_mfr <- as.formula(paste("I(log(SALEPRICE)) ~ h_baths + f_baths + n_fireplaces +
     pct_canopy_cov + dist_ugb + UNITS +
     dist_cityhall + YEARBUILT + CN_score + BLDGSQFT + 
     AREA + garage_sqft + attic_dum + avgheight + year_sold + ",
                                constraints.form))

m2 <- lm(formula_mfr, data = trim %>% 
           filter(prop_type == "Multi-family"))

summary(m2)
```


## Using E-net on all variables 
We have missing data, so e-net can't be run.
```{r}
enet_df <- trim %>%
  select(-matches("val|date|grade|arms_length|shared|source|SITEADDR|owner|X1|state_id"))

set.seed(42)
cv_5 <- trainControl(method = "cv", number = 5)

hit_elnet <- train(I(log(SALEPRICE)) ~ ., data = enet_df,
  method = "glmnet",
  trControl = cv_5, 
  na.action = na.omit)

```




