---
title: "Cleaning everything"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CLEANING EVERYTHING
```{r}
library(tidyverse)
library(readxl)
df <- read_csv("./DATA/thesis-data.csv")
```

Note that the isVacant variable from the capacity data frame is equal to 1 when partially or fully vacant, so a value of 1 makes sense, however may not be super useful for our purposes (it'd be better to have 0/1 partially or not vacant v. fully vacant).

May want to check out some of these properties on a map to understand what is vacant is capturing & whether or not we want to keep it in the analysis.
```{r}
summary(df$percent_vacant)
summary(df$SALEPRICE)
table(df$prop_type)

df %>% 
  select(contains("con")) %>%
  select(-contains("CONCRETE|SECOND|only|pct")) %>%
  colSums(na.rm = T)
```



From the table above, we have 27,200 SFR, 4,792 MFR, and 2,008 mixed use properties.

# Which transactions are arms-length?
```{r}
assvalue <- df %>% select(STATE_ID, SITEADDR, MKTVALYR1, 
                          LANDVAL1, MKTVALYR2, LANDVAL2, 
                          MKTVALYR3, LANDVAL3, SALEPRICE, 
                          saledate, everything()) %>%
  mutate(diff = SALEPRICE - LANDVAL3, 
         ratio = SALEPRICE/LANDVAL3 * 100)

assvalue %>%
  filter(ratio < 20) %>%
  select(SALEPRICE, ratio, diff, everything()) %>%
  arrange(ratio)

asstrim <- assvalue %>%
  filter(ratio > 20 & PRPCD_DESC != "VACANT LAND")

ggplot(data = assvalue, aes(ratio)) + 
  geom_histogram() +
  xlim(0, 150)

ggplot(data = assvalue, aes(ratio)) + 
  geom_density() +
  xlim(0, 150)

dim(assvalue %>% filter(SALEPRICE == 0))

# SAMPLE LOT THAT HAS TINY RATIO
df %>% filter(STATE_ID == "1S1E17CA  2200")

df %>% filter(grepl("LEVY", SITEADDR))
# could use the variable PRPCD_DESC to help us remove some of the outliers
# note that htis is zoned within SFR, weird i guess it's just undeveloped.  
```

There are 516 properties in our sample that sold for $0. Also what does levy code 001 mean? Should we remove these? It appears from Portlandmaps.com that these are lots that do not have buildings. 

Also note that the `PRPCD_DESC` variable says "VACANT LAND" so we may be able to filter out the vacant parcels by filtering based upon this. If the `isVacant` variable is not as helpful (from  the capacity layer), we could even reconstruct that variable to utilize `PRPCD_DESC` instead. 

```{r}
vaca <- asstrim %>% filter(grepl("VACANT", PRPCD_DESC)) %>%
  select(PRPCD_DESC, STATE_ID, SALEPRICE, prop_type)

unique(vaca$PRPCD_DESC)
```

According to the above table, there are 1289 properties coded as "VACANT LAND" or "IMPROVED LAND AS VACANT".    

### Distribution of sale price

```{R}
saleprice_plot <- ggplot(data = asstrim, aes(SALEPRICE)) + 
  geom_histogram() + 
  xlim(0, 1200000)

saleprice_plot
saleprice_density <- ggplot(data = asstrim, aes(SALEPRICE)) + 
  geom_density() + 
  xlim(0, 1200000)
saleprice_density

summary(asstrim$SALEPRICE)
  
```


# Filling NA constraints with zero

```{R}
asstrim %>%
  select(starts_with("con")) %>%
  colSums(na.rm = T)

setZero <- function(x){ifelse(is.na(x), 0, x)}

const_names <- colnames(asstrim)[grepl("con", colnames(asstrim))][1:27]

asstrim %<>%
  mutate_at(const_names, setZero)
  
```


### Explore the IS_VACANT variable

According to the BLI model, this variable includes both partially and fully vacant lots. The `capacity.full` dataframe has only 34,298 observations (before it is pruned to the taxlots in our analysis). Let's check out the proportion of these that are flagged vacant.

19159/34298 properties are flagged as `vacant.` 

4634 are flagged as surrounded by 100% partially or fully vacant lots.

```{r}
dim(capacity.full)
capacity.full %>% filter(IS_VACANT == "True") %>% dim()

capacity.full %>%
  filter(IS_VACANT == "True" & BLDFT_SQFT > 0) %>%
  select(IS_VACANT, STATE_ID, UNDEV_SQFT, BLDFT_SQFT, ABLD_SQFT) %>%
  slice(980:1000) %>%
  mapview()
  
full_vac <- asstrim %>%
  filter(percent_vacant == 1)

taxlots_pruned %>%
  filter(STATE_ID == "1S2E08CD  23300") %>%
  mapview()
```


### Find and remove land trusts

There are 116 observations where we have "TRUST" in either OWNER1, 2 or 3. 
```{r}
sus.trusts <- assvalue %>%
  filter(grepl("TRUST", OWNER1) | grepl("TRUST", OWNER2) | grepl("TRUST", OWNER3)) %>%
  select(OWNER1, SALEPRICE, LANDVAL3, STATE_ID) %>% 
  pull(SALEPRICE)

asstrim %<>%
  mutate(proud =  grepl("PROUD", OWNER1) | grepl("PROUD", OWNER2) | grepl("PROUD", OWNER3))

asstrim %>%
  filter(trust == T) %>%
  select(OWNER1, SALEPRICE, SITEADDR) 
summary(sus.trusts)
asstrim  %>%
 # mutate(quant = quantile(SALEPRICE, .90)) +
  ggplot(aes(SALEPRICE, fill = trust)) + geom_density() + 
  xlim(0, 2000000)a

```



