---
title: "Pretty_SFR"
output:
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import Packages + Read in Data

```{r, include = TRUE}
library(tidyverse)
library(magrittr)
library(here)
library(data.table)
library(MASS)
library(xtable)
library(knitr)
library(stargazer)
library(pander)
library(kableExtra)
library(lubridate)

# read in csv
thesis_data <- read_csv(here::here("DATA","thesis-data.csv"))
```


```{r, echo = TRUE}
# Split Data
SFR <- thesis_data %>%
  filter(PRPCD_DESC == "RESIDENTIAL IMPROVED", prop_type == "Single-family")

# Clean SFR Dataframe
test1 <- SFR %>%
  dplyr::select(-c(OWNER2, OWNER3, OWNERZIP, 
            MKTVALYR1, MKTVALYR2,
            BLDGVAL1, BLDGVAL2,
            LANDVAL1, LANDVAL2,  
            TOTALVAL1, TOTALVAL2,
            MS_GRADE, ES_GRADE,
            LEGAL_DESC, TAXCODE, PROP_CODE, LANDUSE, BEDROOMS, ACC_STATUS, NAME, COMMPLAN, SHARED, COALIT, HORZ_VERT, AUDIT_NBRH, MIDDLE_SCH,  Category, SOURCE, FRONTAGE, COUNTY, YEARBUILT, bldgtype)) %>%
  mutate(top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
         MKTVALYR3 = case_when(MKTVALYR3 != 2018 ~ 2017, 
                                         TRUE ~ 2018),
         price_diff = SALEPRICE - LANDVAL3, 
         price_ratio = SALEPRICE/LANDVAL3 * 100,
         vacant_dummy = PRPCD_DESC == "VACANT LAND",
         llc_flag = grepl("LLC", OWNER1),
         proud_flag =  grepl("PROUD", OWNER1),
         trust_flag = grepl("TRUST", OWNER1) & !grepl("FAMILY", OWNER1) & !grepl("LIVING", OWNER1)) %>%
  mutate(arms_length = price_ratio > 20,
         yearbuilt = na_if(yearbuilt, 0))

# switch the NAs in the constraints to 0s
to0 <- function(x){ifelse(is.na(x), 0, x)}

# Make a string of constraints and percent canopy names called "con_names"
clean <- SFR %>%
  dplyr::select(contains("con"), contains("pct")) %>%
  dplyr::select(-c("CONCRETE", "FIN SECOND", "PAVING/CONCRETE ONLY", "UNF SECOND", "conFldway", "pct_conFldway")) 
clean_names <- names(clean)
con_names <- paste(clean_names, collapse = " + ")

# removing observations 
dat1 <- test1 %>% #25,266
  mutate_at(vars(clean_names), to0) %>%
  filter(top_1 == FALSE, #25,013, #253
         arms_length == TRUE, #24,495 #472
         vacant_dummy == FALSE, #24,495 #0
         proud_flag == FALSE, #24,480 #15
         llc_flag == FALSE, #24,128 #413
         trust_flag == FALSE #24,081 #52
  )

#garage sqft
gar_sqft_sum <- dat1 %>%
  dplyr::select(matches("gar"), matches("car")) %>%
  rowSums()

#deck/patio/porch sqft
deck_sqft_sum <- dat1 %>%
  dplyr::select(matches("deck"), matches("patio"), matches("porch")) %>%
  rowSums()

# attic sqft
attic_sqft_sum <- dat1 %>%
  dplyr::select(matches("attic")) %>%
  rowSums()

# basement sqft
bsmt_sqft_sum <- dat1 %>%
  dplyr::select(matches("bsmt")) %>%
  dplyr::select(-c("BSMT PARKING","BSMT GAR")) %>%
  rowSums()

# creating zone change dummy
zone_test <- dat1 %>% 
  dplyr::select(STATE_ID, matches("zone"), -c(ZONE_DESC_aug2016, ZONE_DESC_aug2018, ZONE_DESC_feb2018, `Zone Description`)) %>%
  mutate_at(vars(-STATE_ID), str_replace, pattern = "R", replacement = "") %>%
  mutate_at(vars(-STATE_ID), funs(as.numeric))

zone_test1 <- zone_test %>%
  mutate_if(is.numeric, rowSums(zone_test)) %>% # this line is causing me problems
    # rowSums is a dumb function doesnt want to play nicely with mutate, even if i specify using mutate_if or mutate_at. manually involves naming the columns inside the row sums. need state id in order to join. c
  mutate(change = rowSums(zone_test)/10,
         zone_change = case_when(change < 20 ~ FALSE,
                                 TRUE ~ TRUE))

# removing zone columns 

# big boi
dat1 %<>%
  dplyr::select(-c(matches("zone"))) %>%
  mutate(garage_sqft = gar_sqft_sum,
         garage_dum = garage_sqft > 0,
         deck_sqft = deck_sqft_sum,
         deck_dum = deck_sqft > 0,
         attic_sqft = attic_sqft_sum,
         attic_dum = attic_sqft > 0,
         bsmt_sqft = bsmt_sqft_sum,
         bsmt_dum = bsmt_sqft > 0,
         saledate = mdy(saledate), 
         year_sold = year(saledate),
         age_sold = year_sold - yearbuilt,
         n_fireplaces = replace_na(n_fireplaces, 0),
         percent_vacant = percent_vacant*100) %>%
  filter(between(totalsqft, 1, 7500), 
         yearbuilt > 1500,
         f_baths < 6,
         BLDGSQFT != 0,
         age_sold > 0)

will <- thesis_data %>% filter(RNO == "R193903290")
# need to check if improvements square feet add up to SQFT 
```


### Exploration

```{r, eval = FALSE, echo = TRUE}

# A Look at the Dataset-------------------------------------------------

controls <- dat1 %>%
  dplyr::select(price_diff, pct_canopy_cov, taxlot_area, age_sold, totalsqft, dist_ugb, dist_cityhall, percent_vacant, f_baths, h_baths, n_fireplaces, 
         SALEPRICE)
nm <- names(controls)

#, ADUdummy, garage_dum, attic_dum, bsmt_dum, deck_dum, MapLabel, HIGH_SCH, CN_score

# Correlation-------------------------------------------------

correlation <- cor(controls, use = "pairwise.complete.obs")
#takes only obs for which both vars are not NA

# Scatterplots-------------------------------------------------

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(y = nm[length(nm)], x = nm[i])) + 
    geom_point(alpha = 0.1) +
    stat_smooth())
}

ggplot(dat1, aes(y = SALEPRICE, x = TOTALVAL3)) + 
    geom_point(alpha = 0.1)

ggplot(dat1, aes(y = log(SALEPRICE), x = taxlot_area)) + 
    geom_point(alpha = 0.1)

# Outliers -- Box Plots-------------------------------------------------

# best for discrete x

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(y = nm[length(nm)], x = nm[i])) + 
    geom_boxplot(alpha = 0.1))
}

# Distribution -- Density Plots---------------------------------

# Now to check the linearity of the variables it is a good practice to plot distribution graph and look for skewness of features. Kernel density estimate (kde) is a quite useful tool for plotting the shape of a distribution.

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(x = nm[i])) + 
    geom_histogram(bins = 50))
}


# Summary Statistics Table ------------------------------------------
sumstat <- dat1 %>%
    # Select and rename
    dplyr::select(
        `Complete Neighborhoods Score (0-100)` = CN_score,
        `Distance to Central Business District (ft)` = dist_cityhall,
        `Distance to Urban Growth Boundary (ft)` = dist_ugb,
        
        `Building Footprint (sqft)` = totalsqft,
        `Taxlot Area (sqft)` = taxlot_area,
        `Age When Sold` = age_sold,
        `Full Baths` = f_baths,
        `Half Baths` = h_baths,
        `Fireplaces` = n_fireplaces,
        
        `Accessible Dwelling Unit Dummy` = ADUdummy,
        `Canopy Cover (%)` = pct_canopy_cov,
        `Vacant Properties in 200ft Radius (%)` = percent_vacant,
        
        `Garage Dummy` = garage_dum,
        `Garage (sqft)` = garage_sqft,
        `Attic Dummy` = attic_dum,
        `Attic (sqft)` = attic_sqft,
        `Basement Dummy` = bsmt_dum,
        `Basement (sqft)` = bsmt_sqft,
        `Deck Dummy` = deck_dum,
        `Deck (sqft)` = deck_sqft
        ) %>%

    # Find the mean, st. dev., min, and max for each variable 
    summarise_all(funs(mean, sd, min, max)) %>%

    # Move summary stats to columns
    gather(key, value, everything()) %>% 
    separate(key, into = c("variable", "stat"), sep = "_") %>%
    spread(stat, value) %>%

    # Set order of summary statistics 
    dplyr::select(variable, mean, sd, min, max) %>%

    # Round all numeric variables to one decimal point
    mutate_if(is.numeric, funs(round(., 1)))

# Write to .txt
write.table(sumstat, file = "sumstats.txt", sep = ",", quote = FALSE, row.names = F)

```


### Pre-analysis Regressions: Dummy Improvements, Neighborhoods, High Schools, CN_score

```{r, echo = TRUE}

# LINEAR REGRESSION-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
sfr_lin = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
sfr_lin_mod <- lm(sfr_lin, dat1)
summary(sfr_lin_mod)

#plot(sfr_lin_mod)



# BOX-COX (LINEAR) REGRESSION--------------------------------------------

bc = boxcox(sfr_lin_mod, lamba = seq(-3, 3, 1))
best_lam = bc$x[which(bc$y == max(bc$y))]
dat1 %<>% 
  mutate(SALEPRICEbc = SALEPRICE^best_lam)

# pre-analysis formula
sfr_bc = formula(paste0("SALEPRICEbc ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# regression
sfr_mod_bc <- lm(sfr_bc, dat1)
summary(sfr_mod_bc)

#plot(sfr_mod_bc)



# SEMI-LOG REGRESSION-------------------------------------------

dat1 %<>% 
  mutate(SALEPRICElog = log(SALEPRICE))

#pre-analysis formula
sfr_log = formula(paste0("SALEPRICElog ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# regression
sfr_mod_log <- lm(sfr_log, dat1)
summary(sfr_mod_log)

#plot(sfr_mod_log)

# OUTPUT-----------------------------------------------------------

stargazer(
  sfr_lin_mod, sfr_mod_log, sfr_mod_bc,
  title = "Three Regression Models Predicting Constraints Effects on Sale Price",
  column.labels = c("Linear", "Semi-Log", "Box-Cox"),
  keep.stat = c("rsq", "adj.rsq"),
  notes.align = "l",
  type="html", out="models.htm"
  )

# stargazer(
#   sfr_lin_mod, sfr_mod_log, sfr_mod_bc,
#   type = "html",
#   title = "Three Regression Models Predicting Constraints Effects on Sale Price",
#   column.labels = c("Linear", "Semi-Log", "Box-Cox"),
#   colnames = FALSE,
#   model.numbers = FALSE,
#   dep.var.caption = " ",
#   dep.var.labels = "Peer rating (1-5 scale)",
#   covariate.labels = c("Ph.D. acceptance rate", "Enrollment"),
#   keep.stat = c("rsq", "f"),
#   notes.align = "l",
#   add.lines = list(c("Corrected AIC", round(AICc(lm.1), 1), round(AICc(lm.2), 1), round(AICc(lm.3), 1))),
#   out = "images/table1.html"
#   )

library(broom)
sfr_mod_bc <- tidy(lm(sfr_bc, dat1))
sfr_mod_log <- tidy(lm(sfr_log, dat1))
sfr_lin_mod <- tidy(lm(sfr_lin, dat1))

all_models <- rbind_list(
    sfr_lin_mod %>% mutate(model = 1),
    sfr_mod_log %>% mutate(model = 2),
    sfr_mod_bc %>% mutate(model = 3))

all_models

ols_table <- all_models %>%
    dplyr::select(-statistic, -p.value) %>%
    mutate_each(funs(round(., 2)), -term) %>% 
    gather(key, value, estimate:std.error) %>%
    spread(model, value) 

ols_table
```

### Regressions 2: Dummy vs. SQFT Improvements

```{r}
# LINEAR REGRESSION DUMMY-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
dummy = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
dummy_mod <- lm(dummy, dat1)
summary(dummy_mod)

#plot(sfr_lin_mod)

# LINEAR REGRESSION SQFT-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
sqft = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
sqft_mod <- lm(sqft, dat1)
summary(sqft_mod)

#plot(sfr.lin.sqft_mod)

# OUTPUT-----------------------------------------------------------

stargazer(dummy_mod, sqft_mod, type="html", out="models_dummy.htm")
# kable(star.1)
# pander(summary(sfr_mod_linear, sfr_mod_log)) 

```


### Switching CN_score, neighborhood, and elementary school, and County??

note that elementary school is included in cn score

```{r}
# PREANALYSIS LINEAR REGRESSION-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
sfr_lin = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
sfr_lin_mod <- lm(sfr_lin, dat1)
summary(sfr_lin_mod)

#plot(sfr_lin_mod)

# ONLY CN_SCORE, no neighborhood, highschool-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
cn = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + ", con_names))

# reg
cn_mod <- lm(cn, dat1)
summary(cn_mod)

#plot(sfr.lin.sqft_mod)


# ONLY NEIGHBORHOOD FIXED EFFECTS, no cn_score, high school-----------------------------

# formula: only dummies, no percent except for percent canopy cover
neighborhood = formula(paste0("SALEPRICE ~ 
                             percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + MapLabel + ", con_names))

# reg
neighborhood_mod <- lm(neighborhood, dat1)
summary(neighborhood_mod)

#plot(sfr.lin.sqft_mod)



# ONLY HIGH SCHOOL, no neighborhood or cn_score-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
hs = formula(paste0("SALEPRICE ~ 
                             percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + HIGH_SCH + ", con_names))

# reg
hs_mod <- lm(hs, dat1)
summary(hs_mod)

#plot(sfr.lin.sqft_mod)


# Replace high school with elementary school, keep all----------------------------------

# formula: only dummies, no percent except for percent canopy cover
es_all = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + MapLabel + ELEM_SCH + ", con_names))

# reg
es_all_mod <- lm(es_all, dat1)
summary(es_all_mod)

# Replace high school with elementary school, remove cn_score and neighborhoods---------

# formula: only dummies, no percent except for percent canopy cover
es = formula(paste0("SALEPRICE ~ 
                             percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_sqft + attic_sqft + bsmt_sqft + deck_sqft + age_sold + ELEM_SCH + ", con_names))

# reg
es_mod <- lm(es, dat1)
summary(es_mod)


#plot(sfr.lin.sqft_mod)
# OUTPUT-----------------------------------------------------------

stargazer(
  sfr_lin_mod, es_all_mod, cn_mod, neighborhood_mod, hs_mod, es_mod, 
  title = "Varying Spatial Effects",
  sep.width = 0,
  column.labels = c("Linear", "Elementary School, all", "Complete Neighborhoods Score", "Neighborhood FE", "High School", "Elementary School"),
  out="models_spatial.htm")

# kable(star.1)
# pander(summary(sfr_mod_linear, sfr_mod_log)) 
```


Adding in LLCs (per Jon’s comments)


```{r}
# PREANALYSIS LINEAR REGRESSION-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
sfr_lin = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
sfr_lin_mod <- lm(sfr_lin, dat1)
summary(sfr_lin_mod)


# ADD IN LLCS--------------------------------------------------------------

dat_llc <- test1 %>% #25,266
  mutate_at(vars(clean_names), to0) %>%
  filter(top_1 == FALSE, #25,013, #253
         arms_length == TRUE, #24,495 #472
         vacant_dummy == FALSE, #24,495 #0
         proud_flag == FALSE, #24,480 #15
         trust_flag == FALSE #24,081 #52
  )

#garage sqft
gar_sqft_sum <- dat_llc %>%
  dplyr::select(matches("gar"), matches("car")) %>%
  rowSums()

#deck/patio/porch sqft
deck_sqft_sum <- dat_llc %>%
  dplyr::select(matches("deck"), matches("patio"), matches("porch")) %>%
  rowSums()

# attic sqft
attic_sqft_sum <- dat_llc %>%
  dplyr::select(matches("attic")) %>%
  rowSums()

# basement sqft
bsmt_sqft_sum <- dat_llc %>%
  dplyr::select(matches("bsmt")) %>%
  dplyr::select(-c("BSMT PARKING","BSMT GAR")) %>%
  rowSums()

dat_llc %<>%
  mutate(garage_sqft = gar_sqft_sum,
         garage_dum = garage_sqft > 0,
         deck_sqft = deck_sqft_sum,
         deck_dum = deck_sqft > 0,
         attic_sqft = attic_sqft_sum,
         attic_dum = attic_sqft > 0,
         bsmt_sqft = bsmt_sqft_sum,
         bsmt_dum = bsmt_sqft > 0,
         saledate = mdy(saledate), 
         year_sold = year(saledate),
         n_fireplaces = replace_na(n_fireplaces, 0)) %>%
  filter(between(totalsqft, 1, 7500), 
         yearbuilt > 1500,
         f_baths < 6,
         BLDGSQFT != 0)


# formula: only dummies, no percent except for percent canopy cover
llc = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
llc_mod <- lm(llc, dat_llc)
summary(llc_mod)


#plot(sfr.lin.sqft_mod)
# OUTPUT-----------------------------------------------------------

stargazer(
  sfr_lin_mod, llc_mod, 
  title = "Varying Spatial Effects",
  column.labels = c("Linear", "LLC all included"),
  out="models_llc.htm")

```

Incorporating zoning history

```{r}


```

PLAYING AROUND WITH VACANT DUMMY VS PERCENT VACANT (AND OTHER PERCENT CONSTRAINTS)


```{r}

```


Control-specific transformations (ie sqft vs sqft-squared)
PLAYING AROUND WITH PRICE RATIO

```{r}
# PREANALYSIS LINEAR REGRESSION-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
dat1 %<>%
  mutate(LOGdist_ugb = ln(dist_ugb),
         LOGdist_cityhall = ln(dist_cityhall),
         SQUAREDtotalsqft = totalsqft*totalsqft
         )


sfr_lin = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + deck_dum + age_sold + MapLabel + HIGH_SCH + ", con_names))

# reg
sfr_lin_mod <- lm(sfr_lin, dat1)
summary(sfr_lin_mod)

#plot(sfr_lin_mod)

```

