---
title: "Mixed Use"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import Packages + Read in Data

```{r, include = FALSE}
library(tidyverse)
library(magrittr)
library(here)
library(data.table)
library(MASS)
library(kableExtra)
library(stargazer)
library(lubridate)

# read in csv
thesis_data <- read_csv(here::here("DATA","thesis-data.csv"))
```


```{r}
# Split Data
MU <- thesis_data %>%
  filter(prop_type == "Mixed Use")

# Clean MU Dataframe
test2 <- MU %>%
  dplyr::select(-c(OWNER2, OWNER3, OWNERZIP, 
            MKTVALYR1, MKTVALYR2,
            BLDGVAL1, BLDGVAL2,
            LANDVAL1, LANDVAL2,  
            TOTALVAL1, TOTALVAL2,
            MS_GRADE, ES_GRADE,
            LEGAL_DESC, TAXCODE, PROP_CODE, LANDUSE, BEDROOMS, ACC_STATUS, NAME, COMMPLAN, SHARED, COALIT, HORZ_VERT, AUDIT_NBRH, MIDDLE_SCH,  Category, SOURCE, FRONTAGE, COUNTY, YEARBUILT, bldgtype)) %>%
  mutate(top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
         MKTVALYR3 = case_when(MKTVALYR3 != 2018 ~ 2017, 
                                         TRUE ~ 2018),
         price_diff = SALEPRICE - LANDVAL3, 
         price_ratio = SALEPRICE/LANDVAL3 * 100,
         vacant_dummy = PRPCD_DESC == "VACANT LAND",
         llc_flag = grepl("LLC", OWNER1),
         proud_flag =  grepl("PROUD", OWNER1),
         trust_flag = grepl("TRUST", OWNER1) & !grepl("FAMILY", OWNER1) & !grepl("LIVING", OWNER1)) %>%
  mutate(arms_length = price_ratio > 20)

# switch the NAs in the constraints to 0s
to0 <- function(x){
  ifelse(is.na(x), 0, x)
  }

# Make a string of constraints and percent canopy names called "con_names"
clean <- MU %>%
  dplyr::select(contains("con"), contains("pct")) %>%
  dplyr::select(-c("CONCRETE", "FIN SECOND", "PAVING/CONCRETE ONLY", "UNF SECOND", "conFldway", "pct_conFldway")) 
clean_names <- names(clean)
con_names <- paste(clean_names, collapse = " + ")

# removing observations 
dat2 <- test2 %>% #2008
  mutate_at(vars(clean_names), to0) %>%
  filter(top_1 == FALSE, #1987 #21
         arms_length == TRUE, #1926 #59
         vacant_dummy == FALSE, #1800 #132
  ) 
  

dsexy <- test2 %>%
  filter(llc_flag == TRUE)


#garage sqft
gar_sqft_sum <- dat2 %>%
  dplyr::select(matches("gar")) %>%
  rowSums()

# attic sqft
attic_sqft_sum <- dat2 %>%
  dplyr::select(matches("attic")) %>%
  rowSums()

# basement sqft
bsmt_sqft_sum <- dat2 %>%
  dplyr::select(matches("bsmt")) %>%
  dplyr::select(-c("BSMT PARKING","BSMT GAR")) %>%
  rowSums()
  
dat2 %<>%
  mutate(garage_sqft = gar_sqft_sum,
         garage_dum = garage_sqft > 0,
         attic_sqft = attic_sqft_sum,
         attic_dum = attic_sqft > 0,
         bsmt_sqft = bsmt_sqft_sum,
         bsmt_dum = bsmt_sqft > 0,
         saledate = mdy(saledate), 
         year_sold = year(saledate)) %>%
  filter(yearbuilt > 1500,
         SALEPRICE < 60000000) # 1339

```


### Exploration

```{r, echo = FALSE}

# A Look at the Dataset-------------------------------------------------

salma <- summary(dat2) # notes in thesis notebook

controls <- dat2 %>%
  dplyr::select(price_diff, pct_canopy_cov, taxlot_area, yearbuilt, totalsqft, dist_ugb, dist_cityhall, percent_vacant, CN_score, 
         SALEPRICE)
nm <- names(controls)

# Correlation-------------------------------------------------

correlation2 <- cor(controls, use = "pairwise.complete.obs")
#takes only obs for which both vars are not NA

# Scatterplots-------------------------------------------------

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(y = nm[length(nm)], x = nm[i])) + 
    geom_point(alpha = 0.1) +
    geom_smooth())
}

ggplot(dat2, aes(y = SALEPRICE, x = TOTALVAL3)) + 
    geom_point(alpha = 0.1)

ggplot(dat2, aes(y = log(SALEPRICE), x = taxlot_area)) + 
    geom_point(alpha = 0.1)

# Distribution -- Density Plots---------------------------------

# Now to check the linearity of the variables it is a good practice to plot distribution graph and look for skewness of features. Kernel density estimate (kde) is a quite useful tool for plotting the shape of a distribution.

for (i in seq_along(nm)) {
  print(names(controls[i]))
  print(ggplot(controls, aes_string(x = nm[i])) + 
    geom_histogram(bins = 50))
}

```



### Regressions

```{r, echo = FALSE}

# LINEAR REGRESSION-----------------------------------------

# formula: only dummies, no percent except for percent canopy cover
mu_lin = formula(paste0("SALEPRICE ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + yearbuilt + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + year_sold + maxheight + FLOORS + UNITS + sale_zone + MapLabel + HIGH_SCH + ", con_names))

# reg
mu_lin_mod <- lm(mu_lin, dat1)
summary(mu_lin_mod)

#plot(mu_lin_mod)



# BOX-COX (LINEAR) REGRESSION--------------------------------------------

bc = boxcox(mu_mod_linear, lamba = seq(-3, 3, 1))
best_lam = bc$x[which(bc$y == max(bc$y))]
dat1 %<>% 
  mutate(SALEPRICEbc = SALEPRICE^best_lam)

# pre-analysis formula
mu_bc = formula(paste0("SALEPRICEbc ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + yearbuilt + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + year_sold + MapLabel + HIGH_SCH + ", con_names))

# regression
mu_mod_bc <- lm(mu_bc, dat1)
summary(mu_mod_bc)

#plot(mu_mod_bc)



# SEMI-LOG REGRESSION-------------------------------------------

dat1 %<>% 
  mutate(SALEPRICElog = log(SALEPRICE))

#pre-analysis formula
mu_log = formula(paste0("SALEPRICElog ~ 
                             CN_score + percent_vacant + dist_cityhall + dist_ugb + totalsqft + yearbuilt + f_baths + h_baths + n_fireplaces + ADUdummy + pct_canopy_cov + taxlot_area + garage_dum + attic_dum + bsmt_dum + year_sold + MapLabel + HIGH_SCH + ", con_names))

# regression
mu_mod_log <- lm(mu_log, dat1)
summary(mu_mod_log)

#plot(mu_mod_log)


#--------------------------------------------------
stargazer(mu_mod_linear, mu_mod_log, mu_mod_bc, type="html", out="models.htm")