---
title: "output"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

-----------------------------------------------------------------------------------
              &nbsp;                Estimate    Std. Error   t value     Pr(>|t|)  
---------------------------------- ----------- ------------ ---------- ------------
         **(Intercept)**            -54877024    1417733      -38.71    1.033e-313 

           **CN_score**              -326.6       105.8       -3.086     0.002033  

        **percent_vacant**            157.7        3277      0.04811      0.9616   

        **dist_cityhall**            -5.649       0.4095      -13.79    4.866e-43  

           **dist_ugb**              -1.235       0.5077      -2.432     0.01503   

          **totalsqft**               60.42       1.339       45.13         0      

          **yearbuilt**               -421        43.11       -9.765    1.841e-22  

           **f_baths**                61342        1382       44.39         0      

           **h_baths**                43987        1746       25.19     1.964e-137 

         **n_fireplaces**             -5666        4249       -1.334      0.1823   

           **ADUdummy**              -35647        7083       -5.033    4.886e-07  

        **pct_canopy_cov**           -13886        4830       -2.875     0.004046  

         **taxlot_area**              1.754       0.123       14.26     7.317e-46  

        **garage_dumTRUE**            12644        2294       5.511     3.622e-08  

        **attic_dumTRUE**             -5226        2097       -2.493     0.01269   

         **bsmt_dumTRUE**             -8739        2175       -4.018    5.903e-05  

          **year_sold**               27884       700.9       39.78         0      

     **MapLabelArbor Lodge**         -16765       22015      -0.7615      0.4464   

   **MapLabelArdenwald-Johnson       -133728      24996       -5.35     8.915e-08  
             Creek**                                                               

    **MapLabelArgay Terrace**        -194366      20873       -9.312    1.413e-20  

  **MapLabelArlington Heights**      -31960       30075       -1.063      0.2879   

     **MapLabelArnold Creek**        -121961      19459       -6.267    3.762e-10  

       **MapLabelAshcreek**          -159885      18899       -8.46     2.894e-17  

  **MapLabelBeaumont-Wilshire**      -10547        9858       -1.07       0.2847   

        **MapLabelBoise**            -18482       30791      -0.6002      0.5484   

 **MapLabelBrentwood-Darlington**    -164267      15699       -10.46     1.53e-25  

      **MapLabelBridlemile**         -178343      25281       -7.055    1.801e-12  

    **MapLabelBrooklyn Action        -133754      18541       -7.214    5.671e-13  
             Corps**                                                               

   **MapLabelBuckman Community       -51339       21719       -2.364      0.0181   
          Association**                                                            

    **MapLabelCathedral Park**        15445       28523       0.5415      0.5882   

  **MapLabelCentennial Community     -166127      19199       -8.653    5.484e-18  
          Association**                                                            

     **MapLabelCollins View**        -160541      20164       -7.962    1.805e-15  

      **MapLabelConcordia**          -37928       13031       -2.911     0.003612  

  **MapLabelCreston-Kenilworth**     -115197      15715       -7.33     2.405e-13  

      **MapLabelCrestwood**          -180351      19883       -9.071    1.314e-19  

  **MapLabelCully Association of     -116518      12252       -9.51     2.164e-21  
           Neighbors**                                                             

    **MapLabelEast Columbia**        -162809      26837       -6.067    1.336e-09  

     **MapLabelEastmoreland**         72107       16223       4.445     8.854e-06  

        **MapLabelEliot**            -154713      47396       -3.264      0.0011   

    **MapLabelFar Southwest**        -126434      20579       -6.144    8.239e-10  

     **MapLabelForest Park**         -67444       28000       -2.409     0.01602   

    **MapLabelFoster-Powell**        -117365      16100       -7.29     3.246e-13  

       **MapLabelGlenfair**          -177227      24989       -7.092    1.374e-12  

      **MapLabelGoose Hollow         -86791       34144       -2.542     0.01103   
        Foothills League**                                                         

      **MapLabelGrant Park**          49076       11356       4.322     1.557e-05  

     **MapLabelHayden Island          50631       36019       1.406       0.1598   
      Neighborhood Network**                                                       

       **MapLabelHayhurst**          -166407      18921       -8.795    1.571e-18  

      **MapLabelHazelwood**          -162153      16446       -9.86     7.195e-23  

    **MapLabelHealy Heights**         -7397       40498      -0.1826      0.8551   

      **MapLabelHillsdale**          -141207      19052       -7.412    1.308e-13  

       **MapLabelHillside**          -39427       28101       -1.403      0.1606   

      **MapLabelHollywood**           37772       24165       1.563       0.118    

      **MapLabelHomestead**          -213267      33149       -6.434    1.281e-10  

   **MapLabelHosford-Abernethy       -26345       15856       -1.662     0.09663   
  Neighborhood District Assn.**                                                    

       **MapLabelHumboldt**          -14894       21901      -0.6801      0.4965   

  **MapLabelIrvington Community       27246       11848        2.3       0.02148   
          Association**                                                            

        **MapLabelKenton**           -38854       24716       -1.572      0.116    

        **MapLabelKerns**            -28755       26923       -1.068      0.2855   

         **MapLabelKing**            -81812       17405       -4.701    2.615e-06  

     **MapLabelLaurelhurst**          40347       10092       3.998     6.422e-05  

        **MapLabelLents**            -163946      15176       -10.8     4.113e-27  

       **MapLabelLinnton**           -181174      32281       -5.612    2.029e-08  

    **MapLabelMadison South**        -119663      13110       -9.128    7.805e-20  

      **MapLabelMaplewood**          -135516      19795       -6.846    7.865e-12  

       **MapLabelMarkham**           -190700      19457       -9.801    1.288e-22  

    **MapLabelMarshall Park**        -145141      21062       -6.891    5.742e-12  

   **MapLabelMC Unclaimed #13**      -142773      93255       -1.531      0.1258   

      **MapLabelMill Park**          -168294      17218       -9.774    1.671e-22  

      **MapLabelMontavilla**         -93567       12547       -7.457    9.268e-14  

   **MapLabelMt. Scott-Arleta**      -112632      16024       -7.029    2.161e-12  

      **MapLabelMt. Tabor**           12612       13583       0.9285      0.3531   

      **MapLabelMultnomah**          -144473      18940       -7.628    2.516e-14  

     **MapLabelNorth Tabor**         -66678       14420       -4.624     3.79e-06  

   **MapLabelNorthwest District       76387       29235       2.613      0.008988  
          Association**                                                            

  **MapLabelNorthwest Heights**      -43922       25924       -1.694     0.09023   

       **MapLabelOverlook**           3727        22738       0.1639      0.8698   

       **MapLabelParkrose**          -197364      21314       -9.26     2.295e-20  

    **MapLabelParkrose Heights       -193427      20637       -9.373    7.964e-21  
    Association of Neighbors**                                                     

       **MapLabelPiedmont**          -39931       21647       -1.845      0.0651   

   **MapLabelPleasant Valley**       -150908      18336       -8.23     2.008e-16  

      **MapLabelPortsmouth**         -36937       25960       -1.423      0.1548   

 **MapLabelPowellhurst-Gilbert**     -161289      17561       -9.184    4.621e-20  

         **MapLabelReed**            -69228       18100       -3.825    0.0001314  

       **MapLabelRichmond**          -27710       14177       -1.955     0.05066   

    **MapLabelRose City Park**       -44194        9576       -4.615    3.962e-06  

       **MapLabelRoseway**           -72157       12158       -5.935    3.001e-09  

       **MapLabelRussell**           -172351      20785       -8.292    1.198e-16  

    **MapLabelSabin Community         -8659       10801      -0.8017      0.4227   
          Association**                                                            

   **MapLabelSellwood-Moreland       -21969       15406       -1.426      0.1539   
       Improvement League**                                                        

   **MapLabelSouth Burlingame**      -162577      20254       -8.027    1.067e-15  

    **MapLabelSouth Portland**       -71414       22183       -3.219     0.001287  

     **MapLabelSouth Tabor**         -72140       15029        -4.8     1.599e-06  

    **MapLabelSouthwest Hills        -57509       25354       -2.268     0.02333   
       Residential League**                                                        

      **MapLabelSt. Johns**          -25685       26001      -0.9878      0.3232   

   **MapLabelSullivan's Gulch**      -106993      23144       -4.623    3.812e-06  

   **MapLabelSumner Association      -186991      23986       -7.796    6.789e-15  
          of Neighbors**                                                           

       **MapLabelSunderland          -142022      61417       -2.312     0.02077   
    Association of Neighbors**                                                     

      **MapLabelSunnyside**          -16775       15981       -1.05       0.2939   

   **MapLabelSylvan-Highlands**      -148423      28330       -5.239    1.634e-07  

   **MapLabelUniversity Park**        -1635       26033      -0.06279     0.9499   

        **MapLabelVernon**            -4451       19178      -0.2321      0.8165   

  **MapLabelWest Portland Park**     -179389      19365       -9.264    2.216e-20  

    **MapLabelWilkes Community       -180145      21832       -8.251    1.683e-16  
             Group**                                                               

    **MapLabelWoodland Park**        -186887      28670       -6.519    7.308e-11  

       **MapLabelWoodlawn**          -45360       19743       -2.298      0.0216   

      **MapLabelWoodstock**          -74500       16273       -4.578    4.727e-06  

     **HIGH_SCHCLEVELAND HS**        -41788       14928       -2.799     0.005126  

   **HIGH_SCHDAVID DOUGLAS HS**      -39065        9155       -4.267    1.992e-05  

     **HIGH_SCHFRANKLIN HS**         -47439       13538       -3.504    0.0004595  

       **HIGH_SCHGRANT HS**          -11066       15973      -0.6928      0.4884   

      **HIGH_SCHGRANT-JEFF**         -77399       23734       -3.261     0.001112  

      **HIGH_SCHLINCOLN HS**          70100       16872       4.155     3.273e-05  

      **HIGH_SCHMADISON HS**         -85110       14767       -5.764    8.386e-09  

     **HIGH_SCHMADISON-JEFF**        -92568       17625       -5.252    1.522e-07  

     **HIGH_SCHPARKROSE HS**         -28197       13848       -2.036     0.04174   

     **HIGH_SCHREYNOLDS HS**         -14311       13662       -1.048      0.2949   

     **HIGH_SCHRIVERDALE HS**        430577       71394       6.031     1.665e-09  

      **HIGH_SCHROOS-JEFF**          -122332      24242       -5.046    4.555e-07  

   **HIGH_SCHROOSEVELT CAMPUS**      -134262      27573       -4.869     1.13e-06  

      **HIGH_SCHSUNSET HS**           79304       33126       2.394      0.01668   

           **conECSI**                90764       1e+05       0.9074      0.3642   

           **conLUST**               -46249       71715      -0.6449      0.519    

           **conHist**                33150        6568       5.048     4.523e-07  

          **conHistLdm**              21555       30674       0.7027      0.4823   

          **conAirHgt**               17427        4247       4.104     4.084e-05  

           **conNoise**               -2359        9408      -0.2507      0.802    

            **conGW**                 46767       53393       0.8759      0.3811   

           **conLSHA**                11138        4037       2.759      0.005807  

           **conSLIDO**              -18738        5978       -3.134     0.001725  

           **conSlp25**               10467        4101       2.552      0.01071   

          **conPrvCom**              275398       100778      2.733      0.006288  

          **conPubOwn**              -12406       40841      -0.3038      0.7613   

           **conSewer**               12342       13013       0.9484      0.3429   

           **conStorm**               -3228        3177       -1.016      0.3097   

          **conTranCap**              -6411        3448       -1.859     0.06302   

          **conTranInt**             -10306        3705       -2.782     0.005413  

          **conTranSub**              -9918        2174       -4.561    5.123e-06  

           **conWater**               -7123        4155       -1.714     0.08647   

          **conCovrly**               -2129        4518      -0.4713      0.6375   

          **conPovrly**              -26435        6268       -4.217    2.484e-05  

          **conWetland**             -65171       24204       -2.693     0.007097  

          **conFld100**              -13044       12437       -1.049      0.2943   

        **pct_conFld100**             18758       19516       0.9611      0.3365   

        **pct_conPovrly**             17496       101216      0.1729      0.8628   

        **pct_conCovrly**             29375        8734       3.363      0.000772  
-----------------------------------------------------------------------------------


--------------------------------------------------------------
 Observations   Residual Std. Error   $R^2$    Adjusted $R^2$ 
-------------- --------------------- -------- ----------------
    16528              99780          0.7585       0.7563     
--------------------------------------------------------------

Table: Fitting linear model: sfr_lin


-----------------------------------------------------------------------------------
              &nbsp;                Estimate    Std. Error   t value     Pr(>|t|)  
---------------------------------- ----------- ------------ ---------- ------------
         **(Intercept)**            -54877024    1417733      -38.71    1.033e-313 

           **conECSI**                90764       1e+05       0.9074      0.3642   

           **conLUST**               -46249       71715      -0.6449      0.519    

           **conHist**                33150        6568       5.048     4.523e-07  

          **conHistLdm**              21555       30674       0.7027      0.4823   

          **conAirHgt**               17427        4247       4.104     4.084e-05  

           **conNoise**               -2359        9408      -0.2507      0.802    

            **conGW**                 46767       53393       0.8759      0.3811   

           **conLSHA**                11138        4037       2.759      0.005807  

           **conSLIDO**              -18738        5978       -3.134     0.001725  

           **conSlp25**               10467        4101       2.552      0.01071   

          **conPrvCom**              275398       100778      2.733      0.006288  

          **conPubOwn**              -12406       40841      -0.3038      0.7613   

           **conSewer**               12342       13013       0.9484      0.3429   

           **conStorm**               -3228        3177       -1.016      0.3097   

          **conTranCap**              -6411        3448       -1.859     0.06302   

          **conTranInt**             -10306        3705       -2.782     0.005413  

          **conTranSub**              -9918        2174       -4.561    5.123e-06  

           **conWater**               -7123        4155       -1.714     0.08647   

          **conCovrly**               -2129        4518      -0.4713      0.6375   

          **conPovrly**              -26435        6268       -4.217    2.484e-05  

          **conWetland**             -65171       24204       -2.693     0.007097  

          **conFld100**              -13044       12437       -1.049      0.2943   

        **pct_conFld100**             18758       19516       0.9611      0.3365   

        **pct_conPovrly**             17496       101216      0.1729      0.8628   

        **pct_conCovrly**             29375        8734       3.363      0.000772  
-----------------------------------------------------------------------------------


--------------------------------------------------------------
 Observations   Residual Std. Error   $R^2$    Adjusted $R^2$ 
-------------- --------------------- -------- ----------------
    16528              99780          0.7585       0.7563     
--------------------------------------------------------------

Table: Fitting linear model: sfr_lin

```{r}
summary(dat1) %>% kable


pretty.table <- mtable("Model 1"=m.01,"Model 2"=m.02,"Model 3"=m.03, summary.stats=c("R-squared","F","p","N"))
pretty.table %>% pander
```

