---
title: "Data Memo for Al"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary statistics

## Import taxlots
```{r message=TRUE, warning=TRUE, include=FALSE}
library(tidyverse)
library(arsenal)
library(readxl)
library(magrittr)
library(kableExtra)
df <- read_csv("/Users/ryankobler/Desktop/thesis/Thesis/DATA/thesis-data.csv")
```
## Clean
```{r}
df %<>%
  mutate(proud_flag =  grepl("PROUD", OWNER1) | grepl("PROUD", OWNER2) | grepl("PROUD", OWNER3),
         trust_flag = grepl("TRUST", OWNER1) | grepl("TRUST", OWNER2) | grepl("TRUST", OWNER3), 
         top_1 =  SALEPRICE > quantile(SALEPRICE, .99),
         price_diff = SALEPRICE - LANDVAL3, 
         price_ratio = SALEPRICE/LANDVAL3 * 100,
         vacant_dummy = PRPCD_DESC == "VACANT LAND") %>%
  mutate(arms_length = price_ratio > 20)

constraints <- c("conWetland", "conNatAm", 
                   "conAirHgt", "conCovrly", "conPovrly", "conHeliprt",
                   "conHist", "conHistLdm", "conInstit", "conLSHA", "conLUST",
                   "conNoise", "conPrvCom", "conSewer", "conSLIDO",
                   "conSlp25", "conStorm", "conTranCap", "conTranSub",
                   "conTranInt", "conTranSub", "conView", "conWater", 
                 "conGW", "conPubOwn", "conFldway", "conFld100", "conECSI")



# switch the NAs in the constraints to 0s
to0 <- function(x){ifelse(is.na(x), 0, x)}


trim <- df %>% 
  filter(proud_flag == F & top_1 == F & 
           arms_length == T & vacant_dummy == F) %>%
  mutate_at(vars(constraints), to0) 

constraint_sums <- trim %>%
  select(constraints) %>%
  rowSums()

trim %<>%
  mutate(is_constrained = constraint_sums > 0)

```

## Tables
Table: Constraint frequency by property type

|                    | Mixed Use (N=1657) | Multi-family (N=4385) | Non-conforming (N=437) | Single-family (N=25752) | Total (N=32231) | p value|
|:-------------------|:------------------:|:---------------------:|:----------------------:|:-----------------------:|:---------------:|-------:|
|**conWetland**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4382 (99.9%)      |      429 (98.2%)       |      25730 (99.9%)      |  32198 (99.9%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      0 (0.0%)      |       3 (0.1%)        |        8 (1.8%)        |        22 (0.1%)        |    33 (0.1%)    |        |
|**conNatAm**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4385 (100.0%)     |      437 (100.0%)      |     25752 (100.0%)      | 32231 (100.0%)  |        |
|**conAirHgt**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1425 (86.0%)    |     3726 (85.0%)      |      285 (65.2%)       |      21120 (82.0%)      |  26556 (82.4%)  |        |
|&nbsp;&nbsp;&nbsp;1 |    232 (14.0%)     |      659 (15.0%)      |      152 (34.8%)       |      4632 (18.0%)       |  5675 (17.6%)   |        |
|**conCovrly**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1633 (98.6%)    |     4326 (98.7%)      |      400 (91.5%)       |      24587 (95.5%)      |  30946 (96.0%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     24 (1.4%)      |       59 (1.3%)       |       37 (8.5%)        |       1165 (4.5%)       |   1285 (4.0%)   |        |
|**conPovrly**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4381 (99.9%)      |      425 (97.3%)       |      25274 (98.1%)      |  31737 (98.5%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      0 (0.0%)      |       4 (0.1%)        |       12 (2.7%)        |       478 (1.9%)        |   494 (1.5%)    |        |
|**conHeliprt**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4385 (100.0%)     |      437 (100.0%)      |     25752 (100.0%)      | 32231 (100.0%)  |        |
|**conHist**         |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1563 (94.3%)    |     4138 (94.4%)      |      435 (99.5%)       |      25081 (97.4%)      |  31217 (96.9%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     94 (5.7%)      |      247 (5.6%)       |        2 (0.5%)        |       671 (2.6%)        |   1014 (3.1%)   |        |
|**conHistLdm**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1632 (98.5%)    |     4369 (99.6%)      |      437 (100.0%)      |      25712 (99.8%)      |  32150 (99.7%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     25 (1.5%)      |       16 (0.4%)       |        0 (0.0%)        |        40 (0.2%)        |    81 (0.3%)    |        |
|**conInstit**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1654 (99.8%)    |     4377 (99.8%)      |      437 (100.0%)      |     25752 (100.0%)      | 32220 (100.0%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      3 (0.2%)      |       8 (0.2%)        |        0 (0.0%)        |        0 (0.0%)         |    11 (0.0%)    |        |
|**conLSHA**         |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1557 (94.0%)    |     4108 (93.7%)      |      399 (91.3%)       |      20932 (81.3%)      |  26996 (83.8%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     100 (6.0%)     |      277 (6.3%)       |       38 (8.7%)        |      4820 (18.7%)       |  5235 (16.2%)   |        |
|**conLUST**         |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1602 (96.7%)    |     4384 (100.0%)     |      407 (93.1%)       |     25748 (100.0%)      |  32141 (99.7%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     55 (3.3%)      |       1 (0.0%)        |       30 (6.9%)        |        4 (0.0%)         |    90 (0.3%)    |        |
|**conNoise**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1565 (94.4%)    |     4291 (97.9%)      |      374 (85.6%)       |      25492 (99.0%)      |  31722 (98.4%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     92 (5.6%)      |       94 (2.1%)       |       63 (14.4%)       |       260 (1.0%)        |   509 (1.6%)    |        |
|**conPrvCom**       |                    |                       |                        |                         |                 |   0.161|
|&nbsp;&nbsp;&nbsp;0 |    1656 (99.9%)    |     4385 (100.0%)     |      437 (100.0%)      |     25750 (100.0%)      | 32228 (100.0%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      1 (0.1%)      |       0 (0.0%)        |        0 (0.0%)        |        2 (0.0%)         |    3 (0.0%)     |        |
|**conSewer**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4385 (100.0%)     |      436 (99.8%)       |      25625 (99.5%)      |  32103 (99.6%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      0 (0.0%)      |       0 (0.0%)        |        1 (0.2%)        |       127 (0.5%)        |   128 (0.4%)    |        |
|**conSLIDO**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1648 (99.5%)    |     4367 (99.6%)      |      429 (98.2%)       |      25304 (98.3%)      |  31748 (98.5%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      9 (0.5%)      |       18 (0.4%)       |        8 (1.8%)        |       448 (1.7%)        |   483 (1.5%)    |        |
|**conSlp25**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1620 (97.8%)    |     4269 (97.4%)      |      424 (97.0%)       |      23883 (92.7%)      |  30196 (93.7%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     37 (2.2%)      |      116 (2.6%)       |       13 (3.0%)        |       1869 (7.3%)       |   2035 (6.3%)   |        |
|**conStorm**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1579 (95.3%)    |     4140 (94.4%)      |      383 (87.6%)       |      23730 (92.1%)      |  29832 (92.6%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     78 (4.7%)      |      245 (5.6%)       |       54 (12.4%)       |       2022 (7.9%)       |   2399 (7.4%)   |        |
|**conTranCap**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4318 (98.5%)      |      431 (98.6%)       |      24028 (93.3%)      |  30434 (94.4%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      0 (0.0%)      |       67 (1.5%)       |        6 (1.4%)        |       1724 (6.7%)       |   1797 (5.6%)   |        |
|**conTranSub**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1482 (89.4%)    |     3523 (80.3%)      |      318 (72.8%)       |      17395 (67.5%)      |  22718 (70.5%)  |        |
|&nbsp;&nbsp;&nbsp;1 |    175 (10.6%)     |      862 (19.7%)      |      119 (27.2%)       |      8357 (32.5%)       |  9513 (29.5%)   |        |
|**conTranInt**      |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1655 (99.9%)    |     4345 (99.1%)      |      436 (99.8%)       |      23677 (91.9%)      |  30113 (93.4%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      2 (0.1%)      |       40 (0.9%)       |        1 (0.2%)        |       2075 (8.1%)       |   2118 (6.6%)   |        |
|**conView**         |                    |                       |                        |                         |                 |   0.969|
|&nbsp;&nbsp;&nbsp;0 |   1657 (100.0%)    |     4385 (100.0%)     |      437 (100.0%)      |     25751 (100.0%)      | 32230 (100.0%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      0 (0.0%)      |       0 (0.0%)        |        0 (0.0%)        |        1 (0.0%)         |    1 (0.0%)     |        |
|**conWater**        |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1574 (95.0%)    |     4124 (94.0%)      |      389 (89.0%)       |      24857 (96.5%)      |  30944 (96.0%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     83 (5.0%)      |      261 (6.0%)       |       48 (11.0%)       |       895 (3.5%)        |   1287 (4.0%)   |        |
|**conGW**           |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1653 (99.8%)    |     4384 (100.0%)     |      434 (99.3%)       |      25730 (99.9%)      |  32201 (99.9%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      4 (0.2%)      |       1 (0.0%)        |        3 (0.7%)        |        22 (0.1%)        |    30 (0.1%)    |        |
|**conPubOwn**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1651 (99.6%)    |     4375 (99.8%)      |      428 (97.9%)       |      25734 (99.9%)      |  32188 (99.9%)  |        |
|&nbsp;&nbsp;&nbsp;1 |      6 (0.4%)      |       10 (0.2%)       |        9 (2.1%)        |        18 (0.1%)        |    43 (0.1%)    |        |
|**conFldway**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1644 (99.2%)    |     4378 (99.8%)      |      427 (97.7%)       |      25702 (99.8%)      |  32151 (99.8%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     13 (0.8%)      |       7 (0.2%)        |       10 (2.3%)        |        50 (0.2%)        |    80 (0.2%)    |        |
|**conFld100**       |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1632 (98.5%)    |     4354 (99.3%)      |      379 (86.7%)       |      25524 (99.1%)      |  31889 (98.9%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     25 (1.5%)      |       31 (0.7%)       |       58 (13.3%)       |       228 (0.9%)        |   342 (1.1%)    |        |
|**conECSI**         |                    |                       |                        |                         |                 | < 0.001|
|&nbsp;&nbsp;&nbsp;0 |    1642 (99.1%)    |     4381 (99.9%)      |      411 (94.1%)       |     25747 (100.0%)      |  32181 (99.8%)  |        |
|&nbsp;&nbsp;&nbsp;1 |     15 (0.9%)      |       4 (0.1%)        |       26 (5.9%)        |        5 (0.0%)         |    50 (0.2%)    |        |

```{r }
# constraints by property type table
constraints_df <- trim %>%
  select(constraints, prop_type) %>%
  mutate_all(as.factor)
const_type_tbl <- tableby(as.formula(paste("prop_type ~ ",
                                       paste(constraints, collapse = " + "))),
                                 data = constraints_df)
x <- summary(const_type_tbl, title = "Constraint frequency by property type")

# zone table
table(trim$sale_zone) %>% kable(caption = "Frequency of Sale Zones") %>%
  kable_styling("striped")

# property type table
table(trim$prop_type) %>% 
  as.data.frame() %>% 
  arrange(desc(Freq)) %>% 
  kable(caption = "Frequency of Property Type") %>%
  kable_styling("striped")
```


## Plots
```{r}
# density plot of sale price by property type
ggplot(trim %>% filter(prop_type != "Non-conforming"),
       aes(log(SALEPRICE), fill = prop_type)) + 
  geom_density() +
  labs(title = "Distribution of sale price", x = "Log price", y = "") + 
  theme_minimal()

# density plot of sale price by whether or not constrained
ggplot(trim %>% filter(prop_type != "Non-conforming"),
       aes(log(SALEPRICE), fill = is_constrained)) + 
  geom_density() +
  labs(title = "Distribution of sale price", x = "Log price", y = "") + 
  theme_minimal()

```


## Control variables
```{r}
controls <- tableby(~ f_baths + h_baths + pct_canopy_cov + CN_score + dist_cityhall +
          dist_ugb + YEARBUILT, data = trim)
controls$control$numeric.stats <- c("Nmiss", 
                                    "meansd", 
                                    "median", 
                                    "range")
#summary(controls, title = "Continuous Controls", digits = 2)
```



|                            |   Overall (N=32231)   |
|:---------------------------|:---------------------:|
|**f_baths**                 |                       |
|&nbsp;&nbsp;&nbsp;N-Miss    |         1859          |
|&nbsp;&nbsp;&nbsp;Mean (SD) |     1.864 (1.180)     |
|&nbsp;&nbsp;&nbsp;Range     |    0.000 - 40.000     |
|**h_baths**                 |                       |
|&nbsp;&nbsp;&nbsp;N-Miss    |         1866          |
|&nbsp;&nbsp;&nbsp;Mean (SD) |     0.351 (0.590)     |
|&nbsp;&nbsp;&nbsp;Range     |    0.000 - 20.000     |
|**pct_canopy_cov**          |                       |
|&nbsp;&nbsp;&nbsp;N-Miss    |         1101          |
|&nbsp;&nbsp;&nbsp;Mean (SD) |     0.282 (0.198)     |
|&nbsp;&nbsp;&nbsp;Range     |     0.000 - 1.000     |
|**CN_score**                |                       |
|&nbsp;&nbsp;&nbsp;Mean (SD) |    58.094 (17.443)    |
|&nbsp;&nbsp;&nbsp;Range     |    1.000 - 100.000    |
|**dist_cityhall**           |                       |
|&nbsp;&nbsp;&nbsp;Mean (SD) | 25274.303 (10161.726) |
|&nbsp;&nbsp;&nbsp;Range     | 1122.948 - 53006.519  |
|**dist_ugb**                |                       |
|&nbsp;&nbsp;&nbsp;Mean (SD) | 18713.615 (7543.791)  |
|&nbsp;&nbsp;&nbsp;Range     |  17.204 - 34315.313   |
|**YEARBUILT**               |                       |
|&nbsp;&nbsp;&nbsp;N-Miss    |          114          |
|&nbsp;&nbsp;&nbsp;Mean (SD) |  1948.780 (335.074)   |
|&nbsp;&nbsp;&nbsp;Range     |   0.000 - 9999.000    |



